---
title: "Pre-processing pipeline"
author: "Loukia Tzavella"
date: "28/01/2019"
output: html_document
---

#### Set up R environment and import data files 

> The scripts for analyses are designed to be run in sequence:
  1. Pre-processing pipeline.Rmd
  2. Pre-registered analyses.Rmd
  3. Robustness checks.Rmd
  
> The scripts should be run in a session open under 'Food_priming.RProj'
> The R environment will include a number of data objects and functions after pre-processing the data.
> These can later be used in analyses scripts. However, if you want to revisit analyses at a later point
  you could save the R environment using the code below.
  save(list = ls(all.names = TRUE), file = here("R_Objects.RData"), envir = .GlobalEnv)


```{r message=FALSE}
# Required R packages are shown below. 
# Please note that the current script has beeen developed under R version 3.4.3
required.packages <- c("BayesFactor", "plyr", "here", "data.table", "jmv", "trimr", "MBESS")
new.packages <- required.packages[!(required.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)>0) {install.packages(required.packages)}

require(BayesFactor)
require(plyr)
require(here)
require(data.table)
require(jmv)
require(trimr)
require(MBESS)
```

* Read csv files from the specified directory and create data lists

```{r}
#Data collected in the laboratory 
lab<- list.files(here("Lab_data"), all.files = TRUE, full.names = FALSE, no.. = TRUE, pattern = "\\.iqdat$")

# Data collected online 
online <- list.files(here("Online_data"), all.files = TRUE, full.names = FALSE, no.. = TRUE, pattern = "\\.iqdat$")

#Save data files
data1<- lapply(here("Lab_data", lab), function(x) {fread(x)})
data1 <- lapply(data1, function(x) as.data.frame(x))

data2 <- lapply(here("Online_data", online), function(x) {fread(x)})
data2 <- lapply(data2, function(x) as.data.frame(x))

#Assign names to the list elements (subject IDs). This is important for created datasets of descriptive statistics. 
#Without list names, there will be no IDs the created data sets.  

subs1 <- lapply(data1, function(x) x[1,1])
names(data1) <- subs1

subs2 <- lapply(data2, function(x) x[1,1])
names(data2) <- subs2
```

* Load functions for data processing and transformations
```{r}
source("Descriptive_functions.R")
```

#### Pre-processing of APP data 

* Process the list of dataframes to select only data from the APP

```{r}
#Select APP blocks and columns of interest

APP1 <- lapply(data1, subset, (blockcode=="APP1" | blockcode=="APP2"), select=c(1:15,28,30,32))
APP2 <- lapply(data2, subset, (blockcode=="APP1" | blockcode=="APP2"), select=c(1:15,28,30,32))

#Remove factor levels that are no longer used 

APP1 <- lapply(APP1, droplevels)
APP2 <- lapply(APP2, droplevels)

#Change the column names 

names <- c("participant","block","trial","response","rt","trial_n","liking","block_n","accuracy",
           "congruence","healthiness","prime_type","prime","target","category","onset2","onset3","onset4")

APP1 <- lapply(APP1, setNames, nm = names)
APP2 <- lapply(APP2, setNames, nm = names)
```

* Inspect data for potential timing errors as pre-registered in the study protocol: 
  
> Timing delays are defined as trial events that last two or more screen refreshes than originally programmed (i.e., >=34 ms delay).
> The trial events to be inspected are the presentation of the prime (233 ms) and mask (17 ms).
> These trials will be removed from analyses. However, if a participant has more than 25% of trials with timing errors, they will then be excluded from all analyses. 
  
```{r}
#Create variables for prime and mask duration (ms)

APP1<- lapply(APP1, transform, prime_ms = onset3-onset2)
APP1<- lapply(APP1, transform, mask_ms = onset4-onset3)

APP2<- lapply(APP2, transform, prime_ms = onset3-onset2)
APP2<- lapply(APP2, transform, mask_ms = onset4-onset3)

#Create variable for timing errors- 1= exclude, 0=include
APP1 <- lapply(APP1, transform, timing = as.integer(ifelse(prime_ms>=283|mask_ms>=67, "1", "0")))
APP2 <- lapply(APP2, transform, timing = as.integer(ifelse(prime_ms>=283|mask_ms>=67, "1", "0")))

#Get proportion of trials to be excluded
APP1_times <- ldply(APP1, function(x) times = mean(x$timing))
APP2_times <- ldply(APP2, function(x) times = mean(x$timing))

#Retrieve IDs for participants who can be included in analyses
APP1_incl <- unique(APP1_times$.id[APP1_times$V1<0.25])
APP2_incl <- unique(APP2_times$.id[APP2_times$V1<0.25])

#Remove trials from the APP data frame lists and original data lists for exclusion of FCT data lists which will be created later in the script
APP1 <- APP1[sapply(APP1, function(x) any(x$participant %in% APP1_incl))]
APP2 <- APP2[sapply(APP2, function(x) any(x$participant %in% APP2_incl))]

data1 <- data1[sapply(data1, function(x) any(x$subject %in% APP1_incl))]
data2 <- data2[sapply(data2, function(x) any(x$subject %in% APP2_incl))]
```

Remove trials with timing delays from the data
```{r}
APP1 <- lapply(APP1, subset, timing==0)
APP2 <- lapply(APP2, subset, timing==0)
```

* Seperate food and non-food prime trials 

```{r}
#Make two subsets for control and food prime trials
nonfood1 <- lapply(APP1, subset, prime_type=="nonfood")
nonfood2 <- lapply(APP2, subset, prime_type=="nonfood")

food1 <- lapply(APP1, subset, prime_type=="food")
food2 <- lapply(APP2, subset, prime_type=="food")
```

* Recode accuracy for all datasets

```{r}
#Recode accuracy values into 0s and 1s for descriptive statistics
#Coding is reversed to get the proportion of error rates (ER); i.e., 1=incorrect; 0=correct
nonfood1<- lapply(nonfood1, transform, accuracy = as.integer(ifelse(accuracy==1, "0", "1")))
nonfood2<- lapply(nonfood2, transform, accuracy = as.integer(ifelse(accuracy==1, "0", "1")))

food1<- lapply(food1, transform, accuracy = as.integer(ifelse(accuracy==1, "0", "1")))
food2<- lapply(food2, transform, accuracy = as.integer(ifelse(accuracy==1, "0", "1")))

#Clear factor levels from subsetted data lists
nonfood1 <- lapply(nonfood1, droplevels)
nonfood2 <- lapply(nonfood2, droplevels)

food1 <- lapply(food1, droplevels)
food2 <- lapply(food2, droplevels)
```

* Apply functions to obtain descriptive statistics and create data frames for analyses

```{r}
#Error rates from non-food trials
nonfood1_ER <- ldply(nonfood1, NF_ER)
nonfood2_ER <- ldply(nonfood2, NF_ER)

#Error rates from food trials
food1_ER <- ldply(food1, F_ER)
food2_ER <- ldply(food2, F_ER)

#Create lists with correct trials
#A new list is introduced here as access to the original list may be needed later on (e.g., data checks)
nonfood1_cor <- lapply(nonfood1, subset, accuracy==0)
nonfood2_cor <- lapply(nonfood2, subset, accuracy==0)

food1_cor <- lapply(food1, subset, accuracy==0)
food2_cor <- lapply(food2, subset, accuracy==0)

#Median RTs of correct trials from non-food trials
nonfood1_RT <- ldply(nonfood1_cor, NF_RT)
nonfood2_RT <- ldply(nonfood2_cor, NF_RT)

#Median RTs of correct trials from food trials
food1_RT <- ldply(food1_cor, F_RT)
food2_RT <- ldply(food2_cor, F_RT)

#Bind both dataframes with descriptives together to get one file for all analyses
nonfood1_app <- cbind(nonfood1_RT, nonfood1_ER)
nonfood2_app <- cbind(nonfood2_RT, nonfood2_ER)

food1_app <- cbind(food1_RT, food1_ER)
food2_app <- cbind(food2_RT, food2_ER)

#Remove duplicate .id column that was created during binding
nonfood1_app <- nonfood1_app[, !duplicated(colnames(nonfood1_app))]
nonfood2_app <- nonfood2_app[, !duplicated(colnames(nonfood2_app))]

food1_app <- food1_app[, !duplicated(colnames(food1_app))]
food2_app <- food2_app[, !duplicated(colnames(food2_app))]
```

* Participants with error rates (ERs) greater or equal to 0.4 in either food or non-food prime trials will be excluded from all respective analyses
  
```{r}
#Get IDs of participants that will be included in analyses based on ER < 0.4
ER1_excl <- unique(c(unique(nonfood1_app$.id[nonfood1_app$ER>=0.4]), unique(food1_app$.id[food1_app$ER>=0.4])))
ER2_excl <- unique(c(unique(nonfood2_app$.id[nonfood2_app$ER>=0.4]), unique(food2_app$.id[food2_app$ER>=0.4])))

#Remove participants from analyses datasets and data1/data2 which will be later pre-processed for FCT analyses
nonfood1_app <- subset(nonfood1_app, !(.id %in% ER1_excl))
nonfood2_app <- subset(nonfood2_app, !(.id %in% ER2_excl))

food1_app <- subset(food1_app, !(.id %in% ER1_excl))
food2_app <- subset(food2_app, !(.id %in% ER2_excl))

data1 <- data1[sapply(data1, function(x) any(!x$subject %in% ER1_excl))]
data2 <- data2[sapply(data2, function(x) any(!x$subject %in% ER2_excl))]
```


* Calculate priming effects for confirmatory analyses

```{r}
#Lab data
food1_app$DRT_h = food1_app$inc_hml_RT - food1_app$con_hml_RT
food1_app$DRT_u = food1_app$inc_uml_RT - food1_app$con_uml_RT

food1_app$DER_h = food1_app$inc_hml_ER - food1_app$con_hml_ER
food1_app$DER_u = food1_app$inc_uml_ER - food1_app$con_uml_ER

food1_app$DRT_hml = food1_app$DRT_u - food1_app$DRT_h

#Online data
food2_app$DRT_h = food2_app$inc_hml_RT - food2_app$con_hml_RT
food2_app$DRT_u = food2_app$inc_uml_RT - food2_app$con_uml_RT

food2_app$DER_h = food2_app$inc_hml_ER - food2_app$con_hml_ER
food2_app$DER_u = food2_app$inc_uml_ER - food2_app$con_uml_ER

food2_app$DRT_hml = food2_app$DRT_u - food2_app$DRT_h
```

* Obtain difference scores for effect size calculation and normality tests

```{r}
#Lab data
food1_app$diff_RT = food1_app$con_RT - food1_app$inc_RT
food1_app$diff_RT_h = food1_app$con_h_RT - food1_app$inc_h_RT
food1_app$diff_RT_u = food1_app$con_u_RT - food1_app$inc_u_RT
food1_app$diff_DRT = food1_app$DRT_h - food1_app$DRT_u

food1_app$diff_ER = food1_app$con_ER - food1_app$inc_ER
food1_app$diff_ER_h = food1_app$con_h_ER - food1_app$inc_h_ER
food1_app$diff_ER_u = food1_app$con_u_ER - food1_app$inc_u_ER
food1_app$diff_DER = food1_app$DER_h - food1_app$DER_u

nonfood1_app$diff_RT = nonfood1_app$con_RT - nonfood1_app$inc_RT
nonfood1_app$diff_ER = nonfood1_app$con_ER - nonfood1_app$inc_ER

#Online data 
food2_app$diff_RT = food2_app$con_RT - food2_app$inc_RT
food2_app$diff_RT_h = food2_app$con_h_RT - food2_app$inc_h_RT
food2_app$diff_RT_u = food2_app$con_u_RT - food2_app$inc_u_RT
food2_app$diff_DRT = food2_app$DRT_h - food2_app$DRT_u

food2_app$diff_ER = food2_app$con_ER - food2_app$inc_ER
food2_app$diff_ER_h = food2_app$con_h_ER - food2_app$inc_h_ER
food2_app$diff_ER_u = food2_app$con_u_ER - food2_app$inc_u_ER
food2_app$diff_DER = food2_app$DER_h - food2_app$DER_u

nonfood2_app$diff_RT = nonfood2_app$con_RT - nonfood2_app$inc_RT
nonfood2_app$diff_ER = nonfood2_app$con_ER - nonfood2_app$inc_ER
```

#### Pre-processing of FCT data 

```{r}
#Select FCT blocks from datasets and selected columns
FCT1 <- lapply(data1, subset, blockcode=="FC_L"|blockcode=="FC_R", select=c(1:5, 16:17, 27,29))
FCT2 <- lapply(data2, subset, blockcode=="FC_L"|blockcode=="FC_R", select=c(1:5, 16:17, 27,29))

#Remove factor levels that are no longer used 
FCT1 <- lapply(FCT1, droplevels)
FCT2 <- lapply(FCT2, droplevels)

#Change the column names 
names2 <- c("participant","block","trial", "response", "rt", "choice", "FCrepeat", "stim1", "stim2")

FCT1 <- lapply(FCT1, setNames, nm = names2)
FCT2 <- lapply(FCT2, setNames, nm = names2)
```

* Pre-registered data exclusion of participants from FCT analyses

> Analyses conducted for H4a, H4b, H4c will not include participants who have more than 50% of missed trials across the two blocks 
  in any trial type examined under H4 (i.e., < 16 out of 32 trials).

> FCrepeat==1 --> participants did not respond initially and the trial was repeated
> FCrepeat==2 --> trial was repeated but participants did not respond again (counts as a 'miss')
> FCrepeat==0 --> participants responded on the trial either initially, or after it was repeated

```{r}
#Haven't accounted for people who quit during the FCT- is this captured for exclusions

#Remove feedback trials (for complete and missed responses) as well as missed trials 
FCT1 <- lapply(FCT1, subset, FCrepeat!=1)
FCT2 <- lapply(FCT2, subset, FCrepeat!=1)

FCT1 <- lapply(FCT1, subset, trial=="HC_ML"|trial=="HC_LL"|trial=="LC_HF"|trial=="LC_UF")
FCT2 <- lapply(FCT2, subset, trial=="HC_ML"|trial=="HC_LL"|trial=="LC_HF"|trial=="LC_UF")

#Recode 'missed response' values into 0s and 1s for mean calculation
#Coding is reversed to get the proportion of missed responses; i.e., 1=missed; 0=completed
FCT1<- lapply(FCT1, transform, response = as.integer(ifelse(response==0, "1", "0")))
FCT2<- lapply(FCT2, transform, response = as.integer(ifelse(response==0, "1", "0")))

#Clear factor levels 
FCT1 <- lapply(FCT1, droplevels)
FCT2 <- lapply(FCT2, droplevels)

#Get proportion of missed responses per trial type
FCT1_miss <- ldply(FCT1, FCT_miss)
FCT2_miss <- ldply(FCT2, FCT_miss)

#V1 = Proportion of missed responses in LC_HF trials
#V2 = Proportion of missed responses in LC_UF trials
#V3 = Proportion of missed responses in HC_ML trials

#Retrieve IDs for participants who can be included in FCT analyses (H4)
FCT1_incl <- unique(FCT1_miss$.id[FCT1_miss$V1<0.25 & FCT1_miss$V2<0.25 & FCT1_miss$V3<0.25])
FCT2_incl <- unique(FCT2_miss$.id[FCT2_miss$V1<0.25 & FCT2_miss$V2<0.25 & FCT2_miss$V3<0.25])

#Remove participants from FCT data frame lists
FCT1 <- FCT1[sapply(FCT1, function(x) any(x$participant %in% FCT1_incl))]
FCT2 <- FCT2[sapply(FCT2, function(x) any(x$participant %in% FCT2_incl))]

#Remove trials from the FCT data frame lists 
FCT1 <- lapply(FCT1, subset, response==0)
FCT2 <- lapply(FCT2, subset, response==0)
```

* Get data frames with FCT outcomes of interest:

> p(most liked|healthy):    probability of selecting a most liked food in most liked vs least liked trials with healthy food pairs
                            trial==LC_HF, choice==HF_ML compared to HF_LL

> p(most liked|unhealthy):  probability of selecting a most liked food in most liked vs least liked trials with unhealthy food pairs
                            trial==LC_UF, choice==UF_ML compared to UF_LL
                          
> p(unhealthy|most liked):  probability of selecting an unhealthy food in unhealthy vs healthy trials with most liked food pairs
                            trial==HC_ML, choice==UF_ML compared to HF_ML
least liked food items in the most liked vs least liked trials when both healthy and unhealthy food pairs are presented, which should be below 0.5 if prime selection according to liking was successful [see also 33].



```{r}
#Recode choices according to trial types with 1s and 0s to get choice probabilities
FCT1 <- lapply(FCT1, transform, choice = ifelse((trial=="LC_HF" & choice=="HF_ML"),"1",
                                         ifelse((trial=="LC_UF" & choice=="UF_ML"),"1",
                                         ifelse((trial=="HC_ML" & choice=="UF_ML"),"1",
                                         ifelse((trial=="HC_LL" & choice=="UF_LL"),"1", "0")))))

FCT2 <- lapply(FCT2, transform, choice = ifelse((trial=="LC_HF" & choice=="HF_ML"),"1",
                                         ifelse((trial=="LC_UF" & choice=="UF_ML"),"1",
                                         ifelse((trial=="HC_ML" & choice=="UF_ML"),"1",
                                         ifelse((trial=="HC_LL" & choice=="UF_LL"),"1", "0")))))

#Change values into integer format 
FCT1 <- lapply(FCT1, transform, choice=as.integer(choice))
FCT2 <- lapply(FCT2, transform, choice=as.integer(choice))

#Apply function for FCT outcomes
FCT1_outcomes <- ldply(FCT1, FCT_p)
FCT2_outcomes <- ldply(FCT2, FCT_p)
```

#### Normality assumption check and data transformations

* Shapiro-Wilk tests for RTs (H1a, H2a-H2d)
```{r warning=FALSE}
#The function saves the p-values from the tests in 'SW_RT'
SW_RT1 <- Shapiro_wilk_RTs(food1_app, nonfood1_app)
SW_RT2 <- Shapiro_wilk_RTs(food2_app, nonfood2_app)

#If the normality assumption is violated for H1a (non-food trials) and predictions under H2 (food trials)
#RTs will be log-transformed accordingly (e.g., H2a violates assumption, then RTs for H2b, H2c and H2d will be transformed as well)

nonfood1_app <- log_H1a(data = nonfood1_app, sw = SW_RT1)
food1_app <- log_H2(data = food1_app, sw = SW_RT1)

nonfood2_app <- log_H1a(data = nonfood2_app, sw = SW_RT2)
food2_app <- log_H2(data = food2_app, sw = SW_RT2)
    
#If RTs are log transformed we will need to recalculate the difference scores- code same as used above
    
food1_app <- log_diff(food1_app)
food2_app <- log_diff(food2_app)
```

<!-- TODO here as well-->

<!--REVIEW this-->

* Shapiro-Wilk tests for ERs (H1b, H3a-H3d)
  
```{r}
# TODO doesn't seem to work on html-- 

#The function saves the p-values from the tests in 'SW_ER'
SW_ER1 <- Shapiro_wilk_ERs(food1_app, nonfood1_app)
SW_ER2 <- Shapiro_wilk_ERs(food2_app, nonfood2_app)

#Bayesian analyses for error rates will be carried out irrespective of the results, but we will report supplementary non-parametric frequentist statistics
#Under 'ttestPS' function from the 'jmv' package we will set the argument "wilcoxon" to TRUE. 

SW_ER1
SW_ER2
```

#### Merging APP and FCT data for analyses

```{r}
#FCT data may have excluded participants that were included in the APP data sets

FCT_app1 <- subset(food1_app, select=c(".id", "DRT_h", "DRT_u", "DRT_hml"))
FCT_app1 <- subset(FCT_app1, .id %in% FCT1_incl)

#if (food2_app$transform=="none") {
#  FCT_app2 <- subset(food2_app, select=c(".id", "DRT_h", "DRT_u", "DRT_hml"))
#} else {
#  FCT_app2 <- subset(food2_app, select=c(".id", "DRT_h_log", "DRT_u_log", "DRT_hml_log"))
#}

FCT_app2 <- subset(food2_app, select=c(".id", "DRT_h", "DRT_u", "DRT_hml"))
FCT_app2 <- subset(FCT_app2, .id %in% FCT2_incl)

#Merge datasets
FCT_full1 <- cbind(FCT_app1, FCT1_outcomes)
FCT_full2 <- cbind(FCT_app2, FCT2_outcomes)

#Remove .id duplicate
FCT_full1 <- FCT_full1[, !duplicated(colnames(FCT_full1))]
FCT_full2 <- FCT_full2[, !duplicated(colnames(FCT_full2))]
```

#### Export created data frames for potential use in later manuscript
```{r}
write.csv(food1_app, "food1_app.csv", row.names=FALSE)
write.csv(food2_app, "food2_app.csv", row.names=FALSE)
write.csv(nonfood1_app, "nonfood1_app.csv", row.names=FALSE)
write.csv(nonfood2_app, "nonfood2_app.csv", row.names=FALSE)

write.csv(FCT_full1, "FCT1.csv", row.names = FALSE)
write.csv(FCT_full2, "FCT2.csv", row.names = FALSE)
```

