---
title: "Pre-registered analyses"
author: "Loukia Tzavella"
date: "28/01/2019"
output: html_document
---

#### Pre-registered Bayesian analyses for laboratory sample

> BF: Bayes factor
> Directional Bayesian paired samples t-tests [-Inf > d > 0]
> rscale="medium" corresponds to √2/2 scale parameter for the half-Cauchy distribution
> Directional Bayesian correlation pairs (positive)
> rscale=1 corresponds to γ=1

* Bayesian paired samples t-tests for H1 [manipulation check]

```{r message=FALSE, warning=FALSE}
if (nonfood1_app$transform == "none") {
  H1a.BF1 <- ttestBF(x = nonfood1_app$con_RT, y = nonfood1_app$inc_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H1a.BF1 <- ttestBF(x = nonfood1_app$logRTcon, y = nonfood1_app$logRTinc, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```
```{r}
H1b.BF1 <- ttestBF(x = nonfood1_app$con_ER, y = nonfood1_app$inc_ER, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
```

```{r}
H1a.BF1
```

```{r}
H1b.BF1
```

* Bayesian paired samples t-tests for H2 [RT priming effects]

```{r message=FALSE, warning=FALSE}
if (food1_app$transform == "none") {
  H2a.BF1 <- ttestBF(x = food1_app$con_RT, y = food1_app$inc_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2a.BF1 <- ttestBF(x = food1_app$logRTcon, y = food1_app$logRTinc, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```
```{r message=FALSE, warning=FALSE}
if (food1_app$transform == "none") {
  H2b.BF1 <- ttestBF(x = food1_app$con_h_RT, y = food1_app$inc_h_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2b.BF1 <- ttestBF(x = food1_app$logRTcon_h, y = food1_app$logRTinc_h, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```
```{r message=FALSE, warning=FALSE}
if (food1_app$transform == "none") {
  H2c.BF1 <- ttestBF(x = food1_app$con_u_RT, y = food1_app$inc_u_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2c.BF1 <- ttestBF(x = food1_app$logRTcon_u, y = food1_app$logRTinc_u, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```
```{r message=FALSE, warning=FALSE}
if (food1_app$transform == "none") {
  H2d.BF1 <- ttestBF(x = food1_app$DRT_h, y = food1_app$DRT_u, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2d.BF1 <- ttestBF(x = food1_app$DRT_h_log, y = food1_app$DRT_u_log, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r}
H2a.BF1
```

```{r}
H2b.BF1
```


```{r}
H2c.BF1
```


```{r}
H2d.BF1
```



* Bayesian paired samples t-tests for H3 [ER priming effects]

```{r message=FALSE}
H3a.BF1 <- ttestBF(x = food1_app$con_ER, y = food1_app$inc_ER, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
H3b.BF1 <- ttestBF(x = food1_app$con_h_ER, y = food1_app$inc_h_ER, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
H3c.BF1 <- ttestBF(x = food1_app$con_u_ER, y = food1_app$inc_u_ER, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
H3d.BF1 <- ttestBF(x = food1_app$DER_h, y = food1_app$DER_u, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
```

```{r}
H3a.BF1
```


```{r}
H3b.BF1
```


```{r}
H3c.BF1
```


```{r}
H3d.BF1
```


* Bayesian correlation pairs forH3 H4 [food choices]
```{r message=FALSE}
H4a.BF1 <- correlationBF(x = FCT_full1$DRT_h, y = FCT_full1$p.mh, rscale = 1, nullInterval = c(0, 1))
H4b.BF1 <- correlationBF(x = FCT_full1$DRT_u, y = FCT_full1$p.mu, rscale = 1, nullInterval = c(0, 1))
H4c.BF1 <- correlationBF(x = FCT_full1$DRT_hml, y = FCT_full1$p.um, rscale = 1, nullInterval = c(0, 1))
```

```{r}
H4a.BF1
```

```{r}
H4b.BF1
```

```{r}
H4c.BF1
```

#### Pre-registered Bayesian analyses for online sample

* Bayesian paired samples t-tests for H1 [manipulation check]

```{r message=FALSE, warning=FALSE}
if (nonfood2_app$transform == "none") {
  H1a.BF2 <- ttestBF(x = nonfood2_app$con_RT, y = nonfood2_app$inc_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H1a.BF2 <- ttestBF(x = nonfood2_app$logRTcon, y = nonfood2_app$logRTinc, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r}
H1b.BF2 <- ttestBF(x = nonfood2_app$con_ER, y = nonfood2_app$inc_ER, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
```

```{r}
H1a.BF2
```


```{r}
H1b.BF2
```



* Bayesian paired samples t-tests for H2 [RT priming effects]

```{r message=FALSE, warning=FALSE}
if (food2_app$transform == "none") {
  H2a.BF2 <- ttestBF(x = food2_app$con_RT, y = food2_app$inc_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2a.BF2 <- ttestBF(x = food2_app$logRTcon, y = food2_app$logRTinc, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```


```{r message=FALSE, warning=FALSE}
if (food2_app$transform == "none") {
  H2b.BF2 <- ttestBF(x = food2_app$con_h_RT, y = food2_app$inc_h_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2b.BF2 <- ttestBF(x = food2_app$logRTcon_h, y = food2_app$logRTinc_h, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```


```{r message=FALSE, warning=FALSE}
if (food2_app$transform == "none") {
  H2c.BF2 <- ttestBF(x = food2_app$con_u_RT, y = food2_app$inc_u_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2c.BF2 <- ttestBF(x = food2_app$logRTcon_u, y = food2_app$logRTinc_u, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```


```{r message=FALSE, warning=FALSE}
if (food2_app$transform == "none") {
  H2d.BF2 <- ttestBF(x = food2_app$DRT_h, y = food2_app$DRT_u, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2d.BF2 <- ttestBF(x = food2_app$DRT_h_log, y = food2_app$DRT_u_log, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```



```{r}
H2a.BF2
```



```{r}
H2b.BF2
```



```{r}
H2c.BF2
```



```{r}
H2d.BF2
```


* Bayesian paired samples t-tests for H3 [ER priming effects]

```{r}
H3a.BF2 <- ttestBF(x = food2_app$con_ER, y = food2_app$inc_ER, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
H3b.BF2 <- ttestBF(x = food2_app$con_h_ER, y = food2_app$inc_h_ER, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
H3c.BF2 <- ttestBF(x = food2_app$con_u_ER, y = food2_app$inc_u_ER, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
H3d.BF2 <- ttestBF(x = food2_app$DER_h, y = food2_app$DER_u, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
```

```{r}
H3a.BF2
```



```{r}
H3b.BF2
```



```{r}
H3c.BF2
```



```{r}
H3d.BF2
```



* Bayesian correlation pairs for H4 [food choices]

```{r}
H4a.BF2 <- correlationBF(x = FCT_full2$DRT_h, y = FCT_full2$p.mh, rscale = 1, nullInterval = c(0, 1))
H4b.BF2 <- correlationBF(x = FCT_full2$DRT_u, y = FCT_full2$p.mu, rscale = 1, nullInterval = c(0, 1))
H4c.BF2 <- correlationBF(x = FCT_full2$DRT_hml, y = FCT_full2$p.um, rscale = 1, nullInterval = c(0, 1))
```

```{r}
H4a.BF2
```

```{r}
H4b.BF2
```

```{r}
H4c.BF2
```

> Note on contigent analyses:

Hypotheses in the opposite direction for H1, H2 and H3 do not need to be analysed separately in this script. The 'ttestBF' function output already includes the BF for the effect in the opposite direction, which can then be reported. 

#### Supplementary frequentist analyses for laboratory sample

> ST: Supplementary test
> Directional frequentist paired samples t-tests [-Inf > d > 0]
> Directional correlation pairs (positive)
> T-test output includes confidence intervals, effect size, mean difference and descriptives

* Frequentist paired samples t-tests for H1 [manipulation check]

```{r warning=FALSE}
if (nonfood1_app$transform == "none") {
  H1a.ST1 <- ttestPS(nonfood1_app, pairs = list(list(i1 = "con_RT", i2 = "inc_RT")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
  print("non-transformed")
} else {
  H1a.ST1 <- ttestPS(nonfood1_app, pairs = list(list(i1 = "logRTcon", i2 = "logRTinc")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
  print("log-transformed")
}
```


```{r}
H1b.ST1 <- ttestPS(nonfood1_app, pairs = list(list(i1 = "con_ER", i2 = "inc_ER")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE, wilcoxon = TRUE)
```


```{r}
H1a.ST1
```

```{r}
H1b.ST1
```

* Frequentist paired samples t-tests for H2 [RT priming effects]

```{r warning=FALSE}
if (food1_app$transform == "none") {
  H2a.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = "con_RT", i2 = "inc_RT")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
  print("non-transformed")
} else {
  H2a.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = "logRTcon", i2 = "logRTinc")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
  print("log-transformed")
}
```

```{r warning=FALSE}
if (food1_app$transform == "none") {
  H2b.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = "con_h_RT", i2 = "inc_h_RT")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)

  print("non-transformed")
} else {
  H2b.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = "logRTcon_h", i2 = "logRTinc_h")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)

  print("log-transformed")
}
```


```{r warning=FALSE}
if (food1_app$transform == "none") {
  H2c.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = "con_u_RT", i2 = "inc_u_RT")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)

  print("non-transformed")
} else {
  H2c.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = "logRTcon_u", i2 = "logRTinc_u")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)

  print("log-transformed")
}
```


```{r warning=FALSE}
if (food1_app$transform == "none") {
  H2d.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = "DRT_u", i2 = "DRT_h")), hypothesis = "oneGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)

  print("non-transformed")
} else {
  H2d.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = "DRT_u_log", i2 = "DRT_h_log")), hypothesis = "oneGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)

  print("log-transformed")
}
```

```{r}
H2a.ST1
```

```{r}
H2b.ST1
```

```{r}
H2c.ST1
```

```{r}
H2d.ST1
```

* Frequentist paired samples t-tests for H3 [ER priming effects]

```{r}
H3a.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = "con_ER", i2 = "inc_ER")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE, wilcoxon = TRUE)
H3b.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = "con_h_ER", i2 = "inc_h_ER")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE, wilcoxon = TRUE)
H3c.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = "con_u_ER", i2 = "inc_u_ER")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE, wilcoxon = TRUE)
H3d.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = "DER_u", i2 = "DER_h")), hypothesis = "oneGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE, wilcoxon = TRUE)
```

```{r}
H3a.ST1
```

```{r}
H3b.ST1
```

```{r}
H3c.ST1
```

```{r}
H3d.ST1
```

* Frequentist correlation pairs for H4 [food choices]

```{r}
H4a.ST1 <- corrMatrix(FCT_full1, vars = c("DRT_h", "p.mh"), hypothesis = "pos", sig = TRUE, ci = TRUE)
H4b.ST1 <- corrMatrix(FCT_full1, vars = c("DRT_u", "p.mu"), hypothesis = "pos", sig = TRUE, ci = TRUE)
H4c.ST1 <- corrMatrix(FCT_full1, vars = c("DRT_hml", "p.um"), hypothesis = "pos", sig = TRUE, ci = TRUE)
```

```{r}
H4a.ST1
```

```{r}
H4b.ST1
```

```{r}
H4c.ST1
```

* Output for two-tailed correlation CIs

The one-tailed CIs are not informative at all because of fixed bounds (e.g. for positive correlations the upper bound is always 1) and therefore we report the two-tailed CIs as implemented in other software to report these in the main manuscript:

```{r}
corrMatrix(FCT_full1, vars = c("DRT_h", "p.mh"), sig = TRUE, ci = TRUE)
corrMatrix(FCT_full1, vars = c("DRT_u", "p.mu"), sig = TRUE, ci = TRUE)
corrMatrix(FCT_full1, vars = c("DRT_hml", "p.um"), sig = TRUE, ci = TRUE)
```

#### Supplementary frequentist analyses for online sample

* Frequentist paired samples t-tests for H1 [manipulation check]

```{r warning=FALSE}
if (nonfood2_app$transform == "none") {
  H1a.ST2 <- ttestPS(nonfood2_app, pairs = list(list(i1 = "con_RT", i2 = "inc_RT")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
  print("non-transformed")
} else {
  H1a.ST2 <- ttestPS(nonfood2_app, pairs = list(list(i1 = "logRTcon", i2 = "logRTinc")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
  print("log-transformed")
}
```

```{r}
H1b.ST2 <- ttestPS(nonfood2_app, pairs = list(list(i1 = "con_ER", i2 = "inc_ER")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE, wilcoxon = TRUE)
```

```{r}
H1a.ST2
```

```{r}
H1b.ST2
```

* Frequentist paired samples t-tests for H2 [RT priming effects]

```{r warning=FALSE}
if (food2_app$transform == "none") {
  H2a.ST2 <- ttestPS(food2_app, pairs = list(list(i1 = "con_RT", i2 = "inc_RT")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
  print("non-transformed")
} else {
  H2a.ST2 <- ttestPS(food2_app, pairs = list(list(i1 = "logRTcon", i2 = "logRTinc")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
  print("log-transformed")
}
```

```{r warning=FALSE}
if (food2_app$transform == "none") {
  H2b.ST2 <- ttestPS(food2_app, pairs = list(list(i1 = "con_h_RT", i2 = "inc_h_RT")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)

  print("non-transformed")
} else {
  H2b.ST2 <- ttestPS(food2_app, pairs = list(list(i1 = "logRTcon_h", i2 = "logRTinc_h")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)

  print("log-transformed")
}
```


```{r warning=FALSE}
if (food2_app$transform == "none") {
  H2c.ST2 <- ttestPS(food2_app, pairs = list(list(i1 = "con_u_RT", i2 = "inc_u_RT")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)

  print("non-transformed")
} else {
  H2c.ST2 <- ttestPS(food2_app, pairs = list(list(i1 = "logRTcon_u", i2 = "logRTinc_u")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)

  print("log-transformed")
}
```


```{r warning=FALSE}
if (food2_app$transform == "none") {
  H2d.ST2 <- ttestPS(food2_app, pairs = list(list(i1 = "DRT_u", i2 = "DRT_h")), hypothesis = "oneGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)

  print("non-transformed")
} else {
  H2d.ST2 <- ttestPS(food2_app, pairs = list(list(i1 = "DRT_u_log", i2 = "DRT_h_log")), hypothesis = "oneGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)

  print("log-transformed")
}
```

```{r}
H2a.ST2
```

```{r}
H2b.ST2
```

```{r}
H2c.ST2
```

```{r}
H2d.ST2
```

* Frequentist paired samples t-tests for H3 [ER priming effects]

```{r}
H3a.ST2 <- ttestPS(food2_app, pairs = list(list(i1 = "con_ER", i2 = "inc_ER")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE, wilcoxon = TRUE)
H3b.ST2 <- ttestPS(food2_app, pairs = list(list(i1 = "con_h_ER", i2 = "inc_h_ER")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE, wilcoxon = TRUE)
H3c.ST2 <- ttestPS(food2_app, pairs = list(list(i1 = "con_u_ER", i2 = "inc_u_ER")), hypothesis = "twoGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE, wilcoxon = TRUE)
H3d.ST2 <- ttestPS(food2_app, pairs = list(list(i1 = "DER_u", i2 = "DER_h")), hypothesis = "oneGreater", meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE, wilcoxon = TRUE)
```

```{r}
H3a.ST2
```

```{r}
H3b.ST2
```

```{r}
H3c.ST2
```

```{r}
H3d.ST2
```

* Frequentist correlation pairs for H4 [food choices]

```{r}
H4a.ST2 <- corrMatrix(FCT_full2, vars = c("DRT_h", "p.mh"), hypothesis = "pos", sig = TRUE, ci = TRUE)
H4b.ST2 <- corrMatrix(FCT_full2, vars = c("DRT_u", "p.mu"), hypothesis = "pos", sig = TRUE, ci = TRUE)
H4c.ST2 <- corrMatrix(FCT_full2, vars = c("DRT_hml", "p.um"), hypothesis = "pos", sig = TRUE, ci = TRUE)
```

```{r}
H4a.ST2
```

```{r}
H4b.ST2
```

```{r}
H4c.ST2
```

* Output for two-tailed correlation CIs

```{r}
corrMatrix(FCT_full2, vars = c("DRT_h", "p.mh"), sig = TRUE, ci = TRUE)
corrMatrix(FCT_full2, vars = c("DRT_u", "p.mu"), sig = TRUE, ci = TRUE)
corrMatrix(FCT_full2, vars = c("DRT_hml", "p.um"), sig = TRUE, ci = TRUE)
```


#### Calculate Cohen's dav for all hypotheses

> The code below has been adapted from https://github.com/Lakens/anchor_based_methods_SESOI/blob/master/effect_size_d_paired_function.R


> Need to create a wrapper function for this to make sure we don't add too many lines of code.
> These could be specific to each hypothesis as the actual data within differ. 

* Calculate standard deviations (SDs) for measures under H1-H3

```{r message=FALSE, warning=FALSE}
# Calculate SDs for all measurements [laboratory]

if (nonfood1_app$transform == "none") {
  H1a.1.sd1 <- sd(nonfood1_app$con_RT)
  H1a.1.sd2 <- sd(nonfood1_app$inc_RT)
} else {
  H1a.1.sd1 <- sd(nonfood1_app$logRTcon)
  H1a.1.sd2 <- sd(nonfood1_app$logRTinc)
}

H1b.1.sd1 <- sd(nonfood1_app$con_ER)
H1b.1.sd2 <- sd(nonfood1_app$inc_ER)

if (food1_app$transform == "none") {
  H2a.1.sd1 <- sd(food1_app$con_RT)
  H2a.1.sd2 <- sd(food1_app$inc_RT)
  H2b.1.sd1 <- sd(food1_app$con_h_RT)
  H2b.1.sd2 <- sd(food1_app$inc_h_RT)
  H2c.1.sd1 <- sd(food1_app$con_u_RT)
  H2c.1.sd2 <- sd(food1_app$inc_u_RT)
  H2d.1.sd1 <- sd(food1_app$DRT_u)
  H2d.1.sd2 <- sd(food1_app$DRT_h)
} else {
  H2a.1.sd1 <- sd(food1_app$logRTcon)
  H2a.1.sd2 <- sd(food1_app$logRTinc)
  H2b.1.sd1 <- sd(food1_app$logRTcon_h)
  H2b.1.sd2 <- sd(food1_app$logRTinc_h)
  H2c.1.sd1 <- sd(food1_app$logRTcon_u)
  H2c.1.sd2 <- sd(food1_app$logRTinc_u)
  H2d.1.sd1 <- sd(food1_app$DRT_u_log)
  H2d.1.sd2 <- sd(food1_app$DRT_h_log)
}

H3a.1.sd1 <- sd(food1_app$con_ER)
H3a.1.sd2 <- sd(food1_app$inc_ER)
H3b.1.sd1 <- sd(food1_app$con_h_ER)
H3b.1.sd2 <- sd(food1_app$inc_h_ER)
H3c.1.sd1 <- sd(food1_app$con_u_ER)
H3c.1.sd2 <- sd(food1_app$inc_u_ER)
H3d.1.sd1 <- sd(food1_app$DER_u)
H3d.1.sd2 <- sd(food1_app$DER_h)

# Calculate SDs for all measurements [online]
if (nonfood2_app$transform == "none") {
  H1a.2.sd1 <- sd(nonfood2_app$con_RT)
  H1a.2.sd2 <- sd(nonfood2_app$inc_RT)
} else {
  H1a.2.sd1 <- sd(nonfood2_app$logRTcon)
  H1a.2.sd2 <- sd(nonfood2_app$logRTinc)
}

H1b.2.sd1 <- sd(nonfood2_app$con_ER)
H1b.2.sd2 <- sd(nonfood2_app$inc_ER)

if (food2_app$transform == "none") {
  H2a.2.sd1 <- sd(food2_app$con_RT)
  H2a.2.sd2 <- sd(food2_app$inc_RT)
  H2b.2.sd1 <- sd(food2_app$con_h_RT)
  H2b.2.sd2 <- sd(food2_app$inc_h_RT)
  H2c.2.sd1 <- sd(food2_app$con_u_RT)
  H2c.2.sd2 <- sd(food2_app$inc_u_RT)
  H2d.2.sd1 <- sd(food2_app$DRT_u)
  H2d.2.sd2 <- sd(food2_app$DRT_h)
} else {
  H2a.2.sd1 <- sd(food2_app$logRTcon)
  H2a.2.sd2 <- sd(food2_app$logRTinc)
  H2b.2.sd1 <- sd(food2_app$logRTcon_h)
  H2b.2.sd2 <- sd(food2_app$logRTinc_h)
  H2c.2.sd1 <- sd(food2_app$logRTcon_u)
  H2c.2.sd2 <- sd(food2_app$logRTinc_u)
  H2d.2.sd1 <- sd(food2_app$DRT_u_log)
  H2d.2.sd2 <- sd(food2_app$DRT_h_log)
}

H3a.2.sd1 <- sd(food2_app$con_ER)
H3a.2.sd2 <- sd(food2_app$inc_ER)
H3b.2.sd1 <- sd(food2_app$con_h_ER)
H3b.2.sd2 <- sd(food2_app$inc_h_ER)
H3c.2.sd1 <- sd(food2_app$con_u_ER)
H3c.2.sd2 <- sd(food2_app$inc_u_ER)
H3d.2.sd1 <- sd(food2_app$DER_u)
H3d.2.sd2 <- sd(food2_app$DER_h)
```

* Calculate mean differences for measures under H1-H3

```{r message=FALSE, warning=FALSE}
# Calculate mean differences for all measurements [laboratory]
if (nonfood1_app$transform == "none") {
  H1a.1.m_diff <- mean(nonfood1_app$diff_RT)
} else {
  H1a.1.m_diff <- mean(nonfood1_app$diff_RT_log)
}

H1b.1.m_diff <- mean(nonfood1_app$diff_ER)

if (food1_app$transform == "none") {
  H2a.1.m_diff <- mean(food1_app$diff_RT)
  H2b.1.m_diff <- mean(food1_app$diff_RT_h)
  H2c.1.m_diff <- mean(food1_app$diff_RT_u)
  H2d.1.m_diff <- mean(food1_app$diff_DRT)
} else {
  H2a.1.m_diff <- mean(food1_app$diff_RT_log)
  H2b.1.m_diff <- mean(food1_app$diff_RT_h_log)
  H2c.1.m_diff <- mean(food1_app$diff_RT_u_log)
  H2d.1.m_diff <- mean(food1_app$diff_DRT_log)
}

H3a.1.m_diff <- mean(food1_app$diff_ER)
H3b.1.m_diff <- mean(food1_app$diff_ER_h)
H3c.1.m_diff <- mean(food1_app$diff_ER_u)
H3d.1.m_diff <- mean(food1_app$diff_DER)

# Calculate mean differences for all measurements [online]

if (nonfood2_app$transform == "none") {
  H1a.2.m_diff <- mean(nonfood2_app$diff_RT)
} else {
  H1a.2.m_diff <- mean(nonfood2_app$diff_RT_log)
}

H1b.2.m_diff <- mean(nonfood2_app$diff_ER)

if (food2_app$transform == "none") {
  H2a.2.m_diff <- mean(food2_app$diff_RT)
  H2b.2.m_diff <- mean(food2_app$diff_RT_h)
  H2c.2.m_diff <- mean(food2_app$diff_RT_u)
  H2d.2.m_diff <- mean(food2_app$diff_DRT)
} else {
  H2a.2.m_diff <- mean(food2_app$diff_RT_log)
  H2b.2.m_diff <- mean(food2_app$diff_RT_h_log)
  H2c.2.m_diff <- mean(food2_app$diff_RT_u_log)
  H2d.2.m_diff <- mean(food2_app$diff_DRT_log)
}

H3a.2.m_diff <- mean(food2_app$diff_ER)
H3b.2.m_diff <- mean(food2_app$diff_ER_h)
H3c.2.m_diff <- mean(food2_app$diff_ER_u)
H3d.2.m_diff <- mean(food2_app$diff_DER)
```

* Calculate average standard deviation of both measures in t-test comparisons as a standardizer

```{r message=FALSE, warning=FALSE}
# Calculate average SD for all measures [laboratory]
H1a.1.s_av <- sqrt((H1a.1.sd1^2 + H1a.1.sd2^2) / 2)
H1b.1.s_av <- sqrt((H1b.1.sd1^2 + H1b.1.sd2^2) / 2)

H2a.1.s_av <- sqrt((H2a.1.sd1^2 + H2a.1.sd2^2) / 2)
H2b.1.s_av <- sqrt((H2b.1.sd1^2 + H2b.1.sd2^2) / 2)
H2c.1.s_av <- sqrt((H2c.1.sd1^2 + H2c.1.sd2^2) / 2)
H2d.1.s_av <- sqrt((H2d.1.sd1^2 + H2d.1.sd2^2) / 2)

H3a.1.s_av <- sqrt((H3a.1.sd1^2 + H3a.1.sd2^2) / 2)
H3b.1.s_av <- sqrt((H3b.1.sd1^2 + H3b.1.sd2^2) / 2)
H3c.1.s_av <- sqrt((H3c.1.sd1^2 + H3c.1.sd2^2) / 2)
H3d.1.s_av <- sqrt((H3d.1.sd1^2 + H3d.1.sd2^2) / 2)

# Calculate average SD for all measures [online]
H1a.2.s_av <- sqrt((H1a.2.sd1^2 + H1a.2.sd2^2) / 2)
H1b.2.s_av <- sqrt((H1b.2.sd1^2 + H1b.2.sd2^2) / 2)

H2a.2.s_av <- sqrt((H2a.2.sd1^2 + H2a.2.sd2^2) / 2)
H2b.2.s_av <- sqrt((H2b.2.sd1^2 + H2b.2.sd2^2) / 2)
H2c.2.s_av <- sqrt((H2c.2.sd1^2 + H2c.2.sd2^2) / 2)
H2d.2.s_av <- sqrt((H2d.2.sd1^2 + H2d.2.sd2^2) / 2)

H3a.2.s_av <- sqrt((H3a.2.sd1^2 + H3a.2.sd2^2) / 2)
H3b.2.s_av <- sqrt((H3b.2.sd1^2 + H3b.2.sd2^2) / 2)
H3c.2.s_av <- sqrt((H3c.2.sd1^2 + H3c.2.sd2^2) / 2)
H3d.2.s_av <- sqrt((H3d.2.sd1^2 + H3d.2.sd2^2) / 2)
```

* Calculate Cohen's dav for all comparisons (H1-H3)

```{r message=FALSE, warning=FALSE}
# Cohen's dav for H1-H3 [laboratory]
H1a.1.d_av <- H1a.1.m_diff / H1a.1.s_av
H1b.1.d_av <- H1b.1.m_diff / H1b.1.s_av

H2a.1.d_av <- H2a.1.m_diff / H2a.1.s_av
H2b.1.d_av <- H2b.1.m_diff / H2b.1.s_av
H2c.1.d_av <- H2c.1.m_diff / H2c.1.s_av
H2d.1.d_av <- H2d.1.m_diff / H2d.1.s_av

H3a.1.d_av <- H3a.1.m_diff / H3a.1.s_av
H3b.1.d_av <- H3b.1.m_diff / H3b.1.s_av
H3c.1.d_av <- H3c.1.m_diff / H3c.1.s_av
H3d.1.d_av <- H3d.1.m_diff / H3d.1.s_av

# Cohen's dav for H1-H3 [online]
H1a.2.d_av <- H1a.2.m_diff / H1a.2.s_av
H1b.2.d_av <- H1b.2.m_diff / H1b.2.s_av

H2a.2.d_av <- H2a.2.m_diff / H2a.2.s_av
H2b.2.d_av <- H2b.2.m_diff / H2b.2.s_av
H2c.2.d_av <- H2c.2.m_diff / H2c.2.s_av
H2d.2.d_av <- H2d.2.m_diff / H2d.2.s_av

H3a.2.d_av <- H3a.2.m_diff / H3a.2.s_av
H3b.2.d_av <- H3b.2.m_diff / H3b.2.s_av
H3c.2.d_av <- H3c.2.m_diff / H3c.2.s_av
H3d.2.d_av <- H3d.2.m_diff / H3d.2.s_av
```


* Calculate CIs for Cohen's dav
```{r message=FALSE, warning=FALSE}
# Number of observations
food1_N <- nrow(food1_app)
nonfood1_N <- nrow(nonfood1_app)

food2_N <- nrow(food2_app)
nonfood2_N <- nrow(nonfood2_app)

# Confidence interval
conf_int <- 0.95

# T-values from performed t-tests
H1a.1.t_val <- as.numeric(H1a.ST1[[1]]$asDF[4])
H1b.1.t_val <- as.numeric(H1b.ST1[[1]]$asDF[4])

H2a.1.t_val <- as.numeric(H2a.ST1[[1]]$asDF[4])
H2b.1.t_val <- as.numeric(H2b.ST1[[1]]$asDF[4])
H2c.1.t_val <- as.numeric(H2c.ST1[[1]]$asDF[4])
H2d.1.t_val <- as.numeric(H2d.ST1[[1]]$asDF[4])

H3a.1.t_val <- as.numeric(H3a.ST1[[1]]$asDF[4])
H3b.1.t_val <- as.numeric(H3b.ST1[[1]]$asDF[4])
H3c.1.t_val <- as.numeric(H3c.ST1[[1]]$asDF[4])
H3d.1.t_val <- as.numeric(H3d.ST1[[1]]$asDF[4])

H1a.2.t_val <- as.numeric(H1a.ST2[[1]]$asDF[4])
H1b.2.t_val <- as.numeric(H1b.ST2[[1]]$asDF[4])

H2a.2.t_val <- as.numeric(H2a.ST2[[1]]$asDF[4])
H2b.2.t_val <- as.numeric(H2b.ST2[[1]]$asDF[4])
H2c.2.t_val <- as.numeric(H2c.ST2[[1]]$asDF[4])
H2d.2.t_val <- as.numeric(H2d.ST2[[1]]$asDF[4])

H3a.2.t_val <- as.numeric(H3a.ST2[[1]]$asDF[4])
H3b.2.t_val <- as.numeric(H3b.ST2[[1]]$asDF[4])
H3c.2.t_val <- as.numeric(H3c.ST2[[1]]$asDF[4])
H3d.2.t_val <- as.numeric(H3d.ST2[[1]]$asDF[4])

# SDs of the difference scores
if (nonfood1_app$transform == "none") {
  H1a.1.s_diff <- sd(nonfood1_app$diff_RT)
} else {
  H1a.1.s_diff <- sd(nonfood1_app$diff_RT_log)
}

H1b.1.s_diff <- sd(nonfood1_app$diff_ER)

if (food1_app$transform == "none") {
  H2a.1.s_diff <- sd(food1_app$diff_RT)
  H2b.1.s_diff <- sd(food1_app$diff_RT_h)
  H2c.1.s_diff <- sd(food1_app$diff_RT_u)
  H2d.1.s_diff <- sd(food1_app$diff_DRT)
} else {
  H2a.1.s_diff <- sd(food1_app$diff_RT_log)
  H2b.1.s_diff <- sd(food1_app$diff_RT_h_log)
  H2c.1.s_diff <- sd(food1_app$diff_RT_u_log)
  H2d.1.s_diff <- sd(food1_app$diff_DRT_log)
}

H3a.1.s_diff <- sd(food1_app$diff_ER)
H3b.1.s_diff <- sd(food1_app$diff_ER_h)
H3c.1.s_diff <- sd(food1_app$diff_ER_u)
H3d.1.s_diff <- sd(food1_app$diff_DER)

if (nonfood2_app$transform == "none") {
  H1a.2.s_diff <- sd(nonfood2_app$diff_RT)
} else {
  H1a.2.s_diff <- sd(nonfood2_app$diff_RT_log)
}

H1b.2.s_diff <- sd(nonfood2_app$diff_ER)

if (food2_app$transform == "none") {
  H2a.2.s_diff <- sd(food2_app$diff_RT)
  H2b.2.s_diff <- sd(food2_app$diff_RT_h)
  H2c.2.s_diff <- sd(food2_app$diff_RT_u)
  H2d.2.s_diff <- sd(food2_app$diff_DRT)
} else {
  H2a.2.s_diff <- sd(food2_app$diff_RT_log)
  H2b.2.s_diff <- sd(food2_app$diff_RT_h_log)
  H2c.2.s_diff <- sd(food2_app$diff_RT_u_log)
  H2d.2.s_diff <- sd(food2_app$diff_DRT_log)
}

H3a.2.s_diff <- sd(food2_app$diff_ER)
H3b.2.s_diff <- sd(food2_app$diff_ER_h)
H3c.2.s_diff <- sd(food2_app$diff_ER_u)
H3d.2.s_diff <- sd(food2_app$diff_DER)

# Confidence limits
H1a.1.limits <- conf.limits.nct(t.value = H1a.1.t_val, df = nonfood1_N - 1, conf.level = conf_int)
H1b.1.limits <- conf.limits.nct(t.value = H1b.1.t_val, df = nonfood1_N - 1, conf.level = conf_int)

H2a.1.limits <- conf.limits.nct(t.value = H2a.1.t_val, df = food1_N - 1, conf.level = conf_int)
H2b.1.limits <- conf.limits.nct(t.value = H2b.1.t_val, df = food1_N - 1, conf.level = conf_int)
H2c.1.limits <- conf.limits.nct(t.value = H2c.1.t_val, df = food1_N - 1, conf.level = conf_int)
H2d.1.limits <- conf.limits.nct(t.value = H2d.1.t_val, df = food1_N - 1, conf.level = conf_int)

H3a.1.limits <- conf.limits.nct(t.value = H3a.1.t_val, df = food1_N - 1, conf.level = conf_int)
H3b.1.limits <- conf.limits.nct(t.value = H3b.1.t_val, df = food1_N - 1, conf.level = conf_int)
H3c.1.limits <- conf.limits.nct(t.value = H3c.1.t_val, df = food1_N - 1, conf.level = conf_int)
H3d.1.limits <- conf.limits.nct(t.value = H3d.1.t_val, df = food1_N - 1, conf.level = conf_int)

H1a.2.limits <- conf.limits.nct(t.value = H1a.2.t_val, df = nonfood2_N - 1, conf.level = conf_int)
H1b.2.limits <- conf.limits.nct(t.value = H1b.2.t_val, df = nonfood2_N - 1, conf.level = conf_int)

H2a.2.limits <- conf.limits.nct(t.value = H2a.2.t_val, df = food2_N - 1, conf.level = conf_int)
H2b.2.limits <- conf.limits.nct(t.value = H2b.2.t_val, df = food2_N - 1, conf.level = conf_int)
H2c.2.limits <- conf.limits.nct(t.value = H2c.2.t_val, df = food2_N - 1, conf.level = conf_int)
H2d.2.limits <- conf.limits.nct(t.value = H2d.2.t_val, df = food2_N - 1, conf.level = conf_int)

H3a.2.limits <- conf.limits.nct(t.value = H3a.2.t_val, df = food2_N - 1, conf.level = conf_int)
H3b.2.limits <- conf.limits.nct(t.value = H3b.2.t_val, df = food2_N - 1, conf.level = conf_int)
H3c.2.limits <- conf.limits.nct(t.value = H3c.2.t_val, df = food2_N - 1, conf.level = conf_int)
H3d.2.limits <- conf.limits.nct(t.value = H3d.2.t_val, df = food2_N - 1, conf.level = conf_int)

# Lower and upper limits for Cohen's dav
# lci: lower CI
# uci: upper CI

H1a.1.d_av_lci <- H1a.1.limits$Lower.Limit * H1a.1.s_diff / (H1a.1.s_av * sqrt(nonfood1_N))
H1a.1.d_av_uci <- H1a.1.limits$Upper.Limit * H1a.1.s_diff / (H1a.1.s_av * sqrt(nonfood1_N))

H1b.1.d_av_lci <- H1b.1.limits$Lower.Limit * H1b.1.s_diff / (H1b.1.s_av * sqrt(nonfood1_N))
H1b.1.d_av_uci <- H1b.1.limits$Upper.Limit * H1b.1.s_diff / (H1b.1.s_av * sqrt(nonfood1_N))

H2a.1.d_av_lci <- H2a.1.limits$Lower.Limit * H2a.1.s_diff / (H2a.1.s_av * sqrt(food1_N))
H2a.1.d_av_uci <- H2a.1.limits$Upper.Limit * H2a.1.s_diff / (H2a.1.s_av * sqrt(food1_N))

H2b.1.d_av_lci <- H2b.1.limits$Lower.Limit * H2b.1.s_diff / (H2b.1.s_av * sqrt(food1_N))
H2b.1.d_av_uci <- H2b.1.limits$Upper.Limit * H2b.1.s_diff / (H2b.1.s_av * sqrt(food1_N))

H2c.1.d_av_lci <- H2c.1.limits$Lower.Limit * H2c.1.s_diff / (H2c.1.s_av * sqrt(food1_N))
H2c.1.d_av_uci <- H2c.1.limits$Upper.Limit * H2c.1.s_diff / (H2c.1.s_av * sqrt(food1_N))

H2d.1.d_av_lci <- H2d.1.limits$Lower.Limit * H2d.1.s_diff / (H2d.1.s_av * sqrt(food1_N))
H2d.1.d_av_uci <- H2d.1.limits$Upper.Limit * H2d.1.s_diff / (H2d.1.s_av * sqrt(food1_N))

H3a.1.d_av_lci <- H3a.1.limits$Lower.Limit * H3a.1.s_diff / (H3a.1.s_av * sqrt(food1_N))
H3a.1.d_av_uci <- H3a.1.limits$Upper.Limit * H3a.1.s_diff / (H3a.1.s_av * sqrt(food1_N))

H3b.1.d_av_lci <- H3b.1.limits$Lower.Limit * H3b.1.s_diff / (H3b.1.s_av * sqrt(food1_N))
H3b.1.d_av_uci <- H3b.1.limits$Upper.Limit * H3b.1.s_diff / (H3b.1.s_av * sqrt(food1_N))

H3c.1.d_av_lci <- H3c.1.limits$Lower.Limit * H3c.1.s_diff / (H3c.1.s_av * sqrt(food1_N))
H3c.1.d_av_uci <- H3c.1.limits$Upper.Limit * H3c.1.s_diff / (H3c.1.s_av * sqrt(food1_N))

H3d.1.d_av_lci <- H3d.1.limits$Lower.Limit * H3d.1.s_diff / (H3d.1.s_av * sqrt(food1_N))
H3d.1.d_av_uci <- H3d.1.limits$Upper.Limit * H3d.1.s_diff / (H3d.1.s_av * sqrt(food1_N))


H1a.2.d_av_lci <- H1a.2.limits$Lower.Limit * H1a.2.s_diff / (H1a.2.s_av * sqrt(nonfood2_N))
H1a.2.d_av_uci <- H1a.2.limits$Upper.Limit * H1a.2.s_diff / (H1a.2.s_av * sqrt(nonfood2_N))

H1b.2.d_av_lci <- H1b.2.limits$Lower.Limit * H1b.2.s_diff / (H1b.2.s_av * sqrt(nonfood2_N))
H1b.2.d_av_uci <- H1b.2.limits$Upper.Limit * H1b.2.s_diff / (H1b.2.s_av * sqrt(nonfood2_N))

H2a.2.d_av_lci <- H2a.2.limits$Lower.Limit * H2a.2.s_diff / (H2a.2.s_av * sqrt(food2_N))
H2a.2.d_av_uci <- H2a.2.limits$Upper.Limit * H2a.2.s_diff / (H2a.2.s_av * sqrt(food2_N))

H2b.2.d_av_lci <- H2b.2.limits$Lower.Limit * H2b.2.s_diff / (H2b.2.s_av * sqrt(food2_N))
H2b.2.d_av_uci <- H2b.2.limits$Upper.Limit * H2b.2.s_diff / (H2b.2.s_av * sqrt(food2_N))

H2c.2.d_av_lci <- H2c.2.limits$Lower.Limit * H2c.2.s_diff / (H2c.2.s_av * sqrt(food2_N))
H2c.2.d_av_uci <- H2c.2.limits$Upper.Limit * H2c.2.s_diff / (H2c.2.s_av * sqrt(food2_N))

H2d.2.d_av_lci <- H2d.2.limits$Lower.Limit * H2d.2.s_diff / (H2d.2.s_av * sqrt(food2_N))
H2d.2.d_av_uci <- H2d.2.limits$Upper.Limit * H2d.2.s_diff / (H2d.2.s_av * sqrt(food2_N))

H3a.2.d_av_lci <- H3a.2.limits$Lower.Limit * H3a.2.s_diff / (H3a.2.s_av * sqrt(food2_N))
H3a.2.d_av_uci <- H3a.2.limits$Upper.Limit * H3a.2.s_diff / (H3a.2.s_av * sqrt(food2_N))

H3b.2.d_av_lci <- H3b.2.limits$Lower.Limit * H3b.2.s_diff / (H3b.2.s_av * sqrt(food2_N))
H3b.2.d_av_uci <- H3b.2.limits$Upper.Limit * H3b.2.s_diff / (H3b.2.s_av * sqrt(food2_N))

H3c.2.d_av_lci <- H3c.2.limits$Lower.Limit * H3c.2.s_diff / (H3c.2.s_av * sqrt(food2_N))
H3c.2.d_av_uci <- H3c.2.limits$Upper.Limit * H3c.2.s_diff / (H3c.2.s_av * sqrt(food2_N))

H3d.2.d_av_lci <- H3d.2.limits$Lower.Limit * H3d.2.s_diff / (H3d.2.s_av * sqrt(food2_N))
H3d.2.d_av_uci <- H3d.2.limits$Upper.Limit * H3d.2.s_diff / (H3d.2.s_av * sqrt(food2_N))
```

### Create tables of Bayesian and frequentist statistics for hypotheses H1-H3

* Laboratory data

```{r}
# Create an empty dataframe to store results
table1 <- as.data.frame(matrix(nrow = 10, ncol = 10))

# Specify hypotheses in first column
table1[1] <- c("H1a", "H1b", "H2a", "H2b", "H2c", "H2d", "H3a", "H3b", "H3c", "H3d")


# Get BF10s from BayesFactor objects and add to second column
table1$V2[1] <- H1a.BF1@bayesFactor[1, 1]
table1$V2[2] <- H1b.BF1@bayesFactor[1, 1]
table1$V2[3] <- H2a.BF1@bayesFactor[1, 1]
table1$V2[4] <- H2b.BF1@bayesFactor[1, 1]
table1$V2[5] <- H2c.BF1@bayesFactor[1, 1]
table1$V2[6] <- H2d.BF1@bayesFactor[1, 1]
table1$V2[7] <- H3a.BF1@bayesFactor[1, 1]
table1$V2[8] <- H3b.BF1@bayesFactor[1, 1]
table1$V2[9] <- H3c.BF1@bayesFactor[1, 1]
table1$V2[10] <- H3d.BF1@bayesFactor[1, 1]

table1$V3 <- c(
  as.numeric(H1a.ST1$ttest$asDF[4]), as.numeric(H1b.ST1$ttest$asDF[4]), as.numeric(H2a.ST1$ttest$asDF[4]),
  as.numeric(H2b.ST1$ttest$asDF[4]), as.numeric(H2c.ST1$ttest$asDF[4]), as.numeric(H2d.ST1$ttest$asDF[4]),
  as.numeric(H3a.ST1$ttest$asDF[4]), as.numeric(H3b.ST1$ttest$asDF[4]), as.numeric(H3c.ST1$ttest$asDF[4]),
  as.numeric(H3d.ST1$ttest$asDF[4])
)

table1$V4 <- c(
  as.numeric(H1a.ST1$ttest$asDF[6]), as.numeric(H1b.ST1$ttest$asDF[6]), as.numeric(H2a.ST1$ttest$asDF[6]),
  as.numeric(H2b.ST1$ttest$asDF[6]), as.numeric(H2c.ST1$ttest$asDF[6]), as.numeric(H2d.ST1$ttest$asDF[6]),
  as.numeric(H3a.ST1$ttest$asDF[6]), as.numeric(H3b.ST1$ttest$asDF[6]), as.numeric(H3c.ST1$ttest$asDF[6]),
  as.numeric(H3d.ST1$ttest$asDF[6])
)

table1$V5 <- c(
  as.numeric(H1a.ST1$ttest$asDF[7]), as.numeric(H1b.ST1$ttest$asDF[7]), as.numeric(H2a.ST1$ttest$asDF[7]),
  as.numeric(H2b.ST1$ttest$asDF[7]), as.numeric(H2c.ST1$ttest$asDF[7]), as.numeric(H2d.ST1$ttest$asDF[7]),
  as.numeric(H3a.ST1$ttest$asDF[7]), as.numeric(H3b.ST1$ttest$asDF[7]), as.numeric(H3c.ST1$ttest$asDF[7]),
  as.numeric(H3d.ST1$ttest$asDF[7])
)

table1$V6 <- c(H1a.1.d_av, H1b.1.d_av, H2a.1.d_av, H2b.1.d_av, H2c.1.d_av, H2d.1.d_av, H3a.1.d_av, H3b.1.d_av, H3c.1.d_av, H3d.1.d_av)

table1$V7 <- c(
  H1a.1.d_av_lci, H1b.1.d_av_lci, H2a.1.d_av_lci, H2b.1.d_av_lci, H2c.1.d_av_lci, H2d.1.d_av_lci, H3a.1.d_av_lci,
  H3b.1.d_av_lci, H3c.1.d_av_lci, H3d.1.d_av_lci
)

table1$V8 <- c(
  H1a.1.d_av_uci, H1b.1.d_av_uci, H2a.1.d_av_uci, H2b.1.d_av_uci, H2c.1.d_av_uci, H2d.1.d_av_uci,
  H3a.1.d_av_uci, H3b.1.d_av_uci, H3c.1.d_av_uci, H3d.1.d_av_uci
)

table1$V9 <- c(
  0, as.numeric(H1b.ST1$ttest$asDF[15]), 0, 0, 0, 0,
  as.numeric(H3a.ST1$ttest$asDF[15]), as.numeric(H3b.ST1$ttest$asDF[15]),
  as.numeric(H3c.ST1$ttest$asDF[15]), as.numeric(H3d.ST1$ttest$asDF[15])
)

table1$V10 <- c(
  0, as.numeric(H1b.ST1$ttest$asDF[16]), 0, 0, 0, 0,
  as.numeric(H3a.ST1$ttest$asDF[16]), as.numeric(H3b.ST1$ttest$asDF[16]),
  as.numeric(H3c.ST1$ttest$asDF[16]), as.numeric(H3d.ST1$ttest$asDF[16])
)


# Add column names to save
names(table1) <- c("Hypothesis", "logBF10", "t", "p", "Mdiff", "dav", "lowerCI", "upperCI", "W", "pw")

table1$p <- ifelse(table1$p < 0.001, "< 0.001", round(table1$p, 3))
table1$pw <- ifelse(table1$pw < 0.001, "< .001", round(table1$pw, 3))


write.csv(table1, "ttests1.csv", row.names = FALSE)
```

* Online data

```{r}
# Create an empty dataframe to store results
table2 <- as.data.frame(matrix(nrow = 10, ncol = 10))

# Specify hypotheses in first column
table2[1] <- c("H1a", "H1b", "H2a", "H2b", "H2c", "H2d", "H3a", "H3b", "H3c", "H3d")

# Get BF10s from BayesFactor objects and add to second column
table2$V2[1] <- H1a.BF2@bayesFactor[1, 1]
table2$V2[2] <- H1b.BF2@bayesFactor[1, 1]
table2$V2[3] <- H2a.BF2@bayesFactor[1, 1]
table2$V2[4] <- H2b.BF2@bayesFactor[1, 1]
table2$V2[5] <- H2c.BF2@bayesFactor[1, 1]
table2$V2[6] <- H2d.BF2@bayesFactor[1, 1]
table2$V2[7] <- H3a.BF2@bayesFactor[1, 1]
table2$V2[8] <- H3b.BF2@bayesFactor[1, 1]
table2$V2[9] <- H3c.BF2@bayesFactor[1, 1]
table2$V2[10] <- H3d.BF2@bayesFactor[1, 1]

table2$V3 <- c(
  as.numeric(H1a.ST2$ttest$asDF[4]), as.numeric(H1b.ST2$ttest$asDF[4]), as.numeric(H2a.ST2$ttest$asDF[4]),
  as.numeric(H2b.ST2$ttest$asDF[4]), as.numeric(H2c.ST2$ttest$asDF[4]), as.numeric(H2d.ST2$ttest$asDF[4]),
  as.numeric(H3a.ST2$ttest$asDF[4]), as.numeric(H3b.ST2$ttest$asDF[4]), as.numeric(H3c.ST2$ttest$asDF[4]),
  as.numeric(H3d.ST2$ttest$asDF[4])
)

table2$V4 <- c(
  as.numeric(H1a.ST2$ttest$asDF[6]), as.numeric(H1b.ST2$ttest$asDF[6]), as.numeric(H2a.ST2$ttest$asDF[6]),
  as.numeric(H2b.ST2$ttest$asDF[6]), as.numeric(H2c.ST2$ttest$asDF[6]), as.numeric(H2d.ST2$ttest$asDF[6]),
  as.numeric(H3a.ST2$ttest$asDF[6]), as.numeric(H3b.ST2$ttest$asDF[6]), as.numeric(H3c.ST2$ttest$asDF[6]),
  as.numeric(H3d.ST2$ttest$asDF[6])
)

table2$V5 <- c(
  as.numeric(H1a.ST2$ttest$asDF[7]), as.numeric(H1b.ST2$ttest$asDF[7]), as.numeric(H2a.ST2$ttest$asDF[7]),
  as.numeric(H2b.ST2$ttest$asDF[7]), as.numeric(H2c.ST2$ttest$asDF[7]), as.numeric(H2d.ST2$ttest$asDF[7]),
  as.numeric(H3a.ST2$ttest$asDF[7]), as.numeric(H3b.ST2$ttest$asDF[7]), as.numeric(H3c.ST2$ttest$asDF[7]),
  as.numeric(H3d.ST2$ttest$asDF[7])
)

table2$V6 <- c(H1a.2.d_av, H1b.2.d_av, H2a.2.d_av, H2b.2.d_av, H2c.2.d_av, H2d.2.d_av, H3a.2.d_av, H3b.2.d_av, H3c.2.d_av, H3d.2.d_av)

table2$V7 <- c(
  H1a.2.d_av_lci, H1b.2.d_av_lci, H2a.2.d_av_lci, H2b.2.d_av_lci, H2c.2.d_av_lci, H2d.2.d_av_lci, H3a.2.d_av_lci,
  H3b.2.d_av_lci, H3c.2.d_av_lci, H3d.2.d_av_lci
)

table2$V8 <- c(
  H1a.2.d_av_uci, H1b.2.d_av_uci, H2a.2.d_av_uci, H2b.2.d_av_uci, H2c.2.d_av_uci, H2d.2.d_av_uci,
  H3a.2.d_av_uci, H3b.2.d_av_uci, H3c.2.d_av_uci, H3d.2.d_av_uci
)

table2$V9 <- c(
  0, as.numeric(H1b.ST2$ttest$asDF[15]), 0, 0, 0, 0,
  as.numeric(H3a.ST2$ttest$asDF[15]), as.numeric(H3b.ST2$ttest$asDF[15]),
  as.numeric(H3c.ST2$ttest$asDF[15]), as.numeric(H3d.ST2$ttest$asDF[15])
)

table2$V10 <- c(
  0, as.numeric(H1b.ST2$ttest$asDF[16]), 0, 0, 0, 0,
  as.numeric(H3a.ST2$ttest$asDF[16]), as.numeric(H3b.ST2$ttest$asDF[16]),
  as.numeric(H3c.ST2$ttest$asDF[16]), as.numeric(H3d.ST2$ttest$asDF[16])
)

names(table2) <- c("Hypothesis", "logBF10", "t", "p", "Mdiff", "dav", "lowerCI", "upperCI", "W", "pw")

table2$p <- ifelse(table2$p < 0.001, "< 0.001", round(table2$p, 3))
table2$pw <- ifelse(table2$pw < 0.001, "< .001", round(table2$pw, 3))

write.csv(table2, "ttests2.csv", row.names = FALSE)
```

