---
title: "Pre-registered analyses"
author: "Loukia Tzavella"
date: "28/01/2019"
output: html_document
---

#### Pre-registered Bayesian analyses for laboratory sample

> BF: Bayes factor
> Directional Bayesian paired samples t-tests [-Inf > d > 0]
> rscale="medium" corresponds to √2/2 scale parameter for the half-Cauchy distribution
> Directional Bayesian correlation pairs (positive)
> rscale=1 corresponds to γ=1

* Bayesian paired samples t-tests for H1 [manipulation check]

```{r}
H1a.BF1 <- ttestBF(x=nonfood1_app$con_RT, y=nonfood1_app$inc_RT, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
H1b.BF1 <- ttestBF(x=nonfood1_app$con_ER, y=nonfood1_app$inc_ER, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
```

```{r}
H1a.BF1
```

```{r}
H1b.BF1
```

* Bayesian paired samples t-tests for H2 [RT priming effects]

```{r}
H2a.BF1 <- ttestBF(x=food1_app$con_RT, y=food1_app$inc_RT, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
H2b.BF1 <- ttestBF(x=food1_app$con_h_RT, y=food1_app$inc_h_RT, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
H2c.BF1 <- ttestBF(x=food1_app$con_u_RT, y=food1_app$inc_u_RT, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
H2d.BF1 <- ttestBF(x=food1_app$DRT_h, y=food1_app$DRT_u, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
```

```{r}
H2a.BF1
```

```{r}
H2b.BF1
```

```{r}
H2c.BF1
```

```{r}
H2d.BF1
```

* Bayesian paired samples t-tests for H3 [ER priming effects]

```{r}
H3a.BF1 <- ttestBF(x=food1_app$con_ER, y=food1_app$inc_ER, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
H3b.BF1 <- ttestBF(x=food1_app$con_h_ER, y=food1_app$inc_h_ER, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
H3c.BF1 <- ttestBF(x=food1_app$con_u_ER, y=food1_app$inc_u_ER, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
H3d.BF1 <- ttestBF(x=food1_app$DER_h, y=food1_app$DER_u, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
```

```{r}
H3a.BF1
```

```{r}
H3b.BF1
```

```{r}
H3c.BF1
```

```{r}
H3d.BF1
```

* Bayesian correlation pairs for H4 [food choices]
```{r}
H4a.BF1 <- correlationBF(x=FCT_full1$DRT_h, y=FCT_full1$p.mh, rscale = 1, nullInterval = c(0, Inf))
H4b.BF1 <- correlationBF(x=FCT_full1$DRT_u, y=FCT_full1$p.mu, rscale = 1, nullInterval = c(0, Inf))
H4c.BF1 <- correlationBF(x=FCT_full1$DRT_hml, y=FCT_full1$p.um, rscale = 1, nullInterval = c(0, Inf))
```

```{r}
H4a.BF1
```

```{r}
H4b.BF1
```

```{r}
H4c.BF1
```

#### Pre-registered Bayesian analyses for online sample

* Bayesian paired samples t-tests for H1 [manipulation check]

```{r}
H1a.BF2 <- ttestBF(x=nonfood2_app$con_RT, y=nonfood2_app$inc_RT, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
H1b.BF2 <- ttestBF(x=nonfood2_app$con_ER, y=nonfood2_app$inc_ER, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
```

```{r}
H1a.BF2
```

```{r}
H1b.BF2
```

* Bayesian paired samples t-tests for H2 [RT priming effects]

```{r}
H2a.BF2 <- ttestBF(x=food2_app$con_RT, y=food2_app$inc_RT, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
H2b.BF2 <- ttestBF(x=food2_app$con_h_RT, y=food2_app$inc_h_RT, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
H2c.BF2 <- ttestBF(x=food2_app$con_u_RT, y=food2_app$inc_u_RT, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
H2d.BF2 <- ttestBF(x=food2_app$DRT_h, y=food2_app$DRT_u, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
```

```{r}
H2a.BF2
```

```{r}
H2b.BF2
```

```{r}
H2c.BF2
```

```{r}
H2d.BF2
```

* Bayesian paired samples t-tests for H3 [ER priming effects]

```{r}
H3a.BF2 <- ttestBF(x=food2_app$con_ER, y=food2_app$inc_ER, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
H3b.BF2 <- ttestBF(x=food2_app$con_h_ER, y=food2_app$inc_h_ER, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
H3c.BF2 <- ttestBF(x=food2_app$con_u_ER, y=food2_app$inc_u_ER, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
H3d.BF2 <- ttestBF(x=food2_app$DER_h, y=food2_app$DER_u, paired=TRUE, rscale="medium", nullInterval = c(-Inf,0))
```

```{r}
H3a.BF2
```

```{r}
H3b.BF2
```

```{r}
H3c.BF2
```

```{r}
H3d.BF2
```

* Bayesian correlation pairs for H4 [food choices]

```{r}
H4a.BF2 <- correlationBF(x=FCT_full2$DRT_h, y=FCT_full2$p.mh, rscale = 1, nullInterval = c(0, Inf))
H4b.BF2 <- correlationBF(x=FCT_full2$DRT_u, y=FCT_full2$p.mu, rscale = 1, nullInterval = c(0, Inf))
H4c.BF2 <- correlationBF(x=FCT_full2$DRT_hml, y=FCT_full2$p.um, rscale = 1, nullInterval = c(0, Inf))
```

```{r}
H4a.BF2
```

```{r}
H4b.BF2
```

```{r}
H4c.BF2
```

> Note on contigent analyses:

> Hypotheses in the opposite direction for H1, H2 and H3 will not need to be analysed separately in this script. 
> The 'ttestBF' function output already includes the BF for the effect in the opposite direction, which can then be reported. 

#### Supplementary frequentist analyses for laboratory sample

> ST: Supplementary test
> Directional frequentist paired samples t-tests [-Inf > d > 0]
> Directional correlation pairs (positive)
> T-test output includes confidence intervals, effect size, mean difference and descriptives

* Frequentist paired samples t-tests for H1 [manipulation check]

```{r}
H1a.ST1 <- ttestPS(nonfood1_app, pairs = list(list(i1 = 'con_RT', i2 = 'inc_RT')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
H1b.ST1 <- ttestPS(nonfood1_app, pairs = list(list(i1 = 'con_ER', i2 = 'inc_ER')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
```

```{r}
H1a.ST1
```

```{r}
H1b.ST1
```

* Frequentist paired samples t-tests for H2 [RT priming effects]

```{r}
H2a.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = 'con_RT', i2 = 'inc_RT')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
H2b.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = 'con_h_RT', i2 = 'inc_h_RT')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
H2c.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = 'con_u_RT', i2 = 'inc_u_RT')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
H2d.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = 'DRT_h', i2 = 'DRT_u')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
```

```{r}
H2a.ST1
```

```{r}
H2b.ST1
```

```{r}
H2c.ST1
```

```{r}
H2d.ST1
```

* Frequentist paired samples t-tests for H3 [ER priming effects]

```{r}
H3a.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = 'con_ER', i2 = 'inc_ER')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
H3b.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = 'con_h_ER', i2 = 'inc_h_ER')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
H3c.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = 'con_u_ER', i2 = 'inc_u_ER')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
H3d.ST1 <- ttestPS(food1_app, pairs = list(list(i1 = 'DER_h', i2 = 'DER_u')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
```

```{r}
H3a.ST1
```

```{r}
H3b.ST1
```

```{r}
H3c.ST1
```

```{r}
H3d.ST1
```

* Frequentist correlation pairs for H4 [food choices]

```{r}
H4a.ST1 <- corrMatrix(FCT_full1, vars=c('DRT_h', 'p.mh'), hypothesis='pos', sig=TRUE, ci=TRUE)
H4b.ST1 <- corrMatrix(FCT_full1, vars=c('DRT_u', 'p.mu'), hypothesis='pos', sig=TRUE, ci=TRUE)
H4c.ST1 <- corrMatrix(FCT_full1, vars=c('DRT_hml', 'p.um'), hypothesis='pos', sig=TRUE, ci=TRUE)
```

```{r}
H4a.ST1
```

```{r}
H4b.ST1
```

```{r}
H4c.ST1
```

#### Supplementary frequentist analyses for online sample

* Frequentist paired samples t-tests for H1 [manipulation check]

```{r}
H1a.ST2 <- ttestPS(nonfood1_app, pairs = list(list(i1 = 'con_RT', i2 = 'inc_RT')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
H1b.ST2 <- ttestPS(nonfood1_app, pairs = list(list(i1 = 'con_ER', i2 = 'inc_ER')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
```

```{r}
H1a.ST2
```

```{r}
H1b.ST2
```

* Frequentist paired samples t-tests for H2 [RT priming effects]

```{r}
H2a.ST2 <- ttestPS(food1_app, pairs = list(list(i1 = 'con_RT', i2 = 'inc_RT')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
H2b.ST2 <- ttestPS(food1_app, pairs = list(list(i1 = 'con_h_RT', i2 = 'inc_h_RT')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
H2c.ST2 <- ttestPS(food1_app, pairs = list(list(i1 = 'con_u_RT', i2 = 'inc_u_RT')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
H2d.ST2 <- ttestPS(food1_app, pairs = list(list(i1 = 'DRT_h', i2 = 'DRT_u')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
```

```{r}
H2a.ST2
```

```{r}
H2b.ST2
```

```{r}
H2c.ST2
```

```{r}
H2d.ST2
```

* Frequentist paired samples t-tests for H3 [ER priming effects]

```{r}
H3a.ST2 <- ttestPS(food1_app, pairs = list(list(i1 = 'con_ER', i2 = 'inc_ER')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
H3b.ST2 <- ttestPS(food1_app, pairs = list(list(i1 = 'con_h_ER', i2 = 'inc_h_ER')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
H3c.ST2 <- ttestPS(food1_app, pairs = list(list(i1 = 'con_u_ER', i2 = 'inc_u_ER')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
H3d.ST2 <- ttestPS(food1_app, pairs = list(list(i1 = 'DER_h', i2 = 'DER_u')), hypothesis = 'twoGreater', meanDiff = TRUE, effectSize = TRUE, ci = TRUE, desc = TRUE)
```

```{r}
H3a.ST1
```

```{r}
H3b.ST1
```

```{r}
H3c.ST1
```

```{r}
H3d.ST1
```

* Frequentist correlation pairs for H4 [food choices]

```{r}
H4a.ST2 <- corrMatrix(FCT_full1, vars=c('DRT_h', 'p.mh'), hypothesis='pos', sig=TRUE, ci=TRUE)
H4b.ST2 <- corrMatrix(FCT_full1, vars=c('DRT_u', 'p.mu'), hypothesis='pos', sig=TRUE, ci=TRUE)
H4c.ST2 <- corrMatrix(FCT_full1, vars=c('DRT_hml', 'p.um'), hypothesis='pos', sig=TRUE, ci=TRUE)
```

```{r}
H4a.ST1
```

```{r}
H4b.ST1
```

```{r}
H4c.ST1
```

#### Calculate Cohen's dav for all hypotheses

> The code below has been adapted from [https://github.com/Lakens/anchor_based_methods_SESOI/blob/master/effect_size_d_paired_function.R](https://github.com/Lakens/anchor_based_methods_SESOI/blob/master/effect_size_d_paired_function.R)

* Calculate standard deviations (SDs) for measures under H1-H3

```{r}
#Calculate SDs for all measurements [laboratory]
H1a.1.sd1 <- sd(nonfood1_app$con_RT)
H1a.1.sd2 <- sd(nonfood1_app$inc_RT)
H1b.1.sd1 <- sd(nonfood1_app$con_ER)
H1b.1.sd2 <- sd(nonfood1_app$inc_ER)

H2a.1.sd1 <- sd(food1_app$con_RT)
H2a.1.sd2 <- sd(food1_app$inc_RT)
H2b.1.sd1 <- sd(food1_app$con_h_RT)
H2b.1.sd2 <- sd(food1_app$inc_h_RT)
H2c.1.sd1 <- sd(food1_app$con_u_RT)
H2c.1.sd2 <- sd(food1_app$inc_u_RT)
H2d.1.sd1 <- sd(food1_app$DRT_h)
H2d.1.sd2 <- sd(food1_app$DRT_u)

H3a.1.sd1 <- sd(food1_app$con_ER)
H3a.1.sd2 <- sd(food1_app$inc_ER)
H3b.1.sd1 <- sd(food1_app$con_h_ER)
H3b.1.sd2 <- sd(food1_app$inc_h_ER)
H3c.1.sd1 <- sd(food1_app$con_u_ER)
H3c.1.sd2 <- sd(food1_app$inc_u_ER)
H3d.1.sd1 <- sd(food1_app$DER_h)
H3d.1.sd2 <- sd(food1_app$DER_u)

#Calculate SDs for all measurements [online]
H1a.2.sd1 <- sd(nonfood2_app$con_RT)
H1a.2.sd2 <- sd(nonfood2_app$inc_RT)
H1b.2.sd1 <- sd(nonfood2_app$con_ER)
H1b.2.sd2 <- sd(nonfood2_app$inc_ER)

H2a.2.sd1 <- sd(food2_app$con_RT)
H2a.2.sd2 <- sd(food2_app$inc_RT)
H2b.2.sd1 <- sd(food2_app$con_h_RT)
H2b.2.sd2 <- sd(food2_app$inc_h_RT)
H2c.2.sd1 <- sd(food2_app$con_u_RT)
H2c.2.sd2 <- sd(food2_app$inc_u_RT)
H2d.2.sd1 <- sd(food2_app$DRT_h)
H2d.2.sd2 <- sd(food2_app$DRT_u)

H3a.2.sd1 <- sd(food2_app$con_ER)
H3a.2.sd2 <- sd(food2_app$inc_ER)
H3b.2.sd1 <- sd(food2_app$con_h_ER)
H3b.2.sd2 <- sd(food2_app$inc_h_ER)
H3c.2.sd1 <- sd(food2_app$con_u_ER)
H3c.2.sd2 <- sd(food2_app$inc_u_ER)
H3d.2.sd1 <- sd(food2_app$DER_h)
H3d.2.sd2 <- sd(food2_app$DER_u)
```

* Calculate mean differences for measures under H1-H3

```{r}
#Calculate mean differences for all measurements [laboratory]
H1a.1.m_diff <- mean(nonfood1_app$diff_RT) 
H1b.1.m_diff <- mean(nonfood1_app$diff_ER)

H2a.1.m_diff <- mean(food1_app$diff_RT)
H2b.1.m_diff <- mean(food1_app$diff_RT_h)
H2c.1.m_diff <- mean(food1_app$diff_RT_u)
H2d.1.m_diff <- mean(food1_app$diff_DRT)

H3a.1.m_diff <- mean(food1_app$diff_ER)
H3b.1.m_diff <- mean(food1_app$diff_ER_h)
H3c.1.m_diff <- mean(food1_app$diff_ER_u)
H3d.1.m_diff <- mean(food1_app$diff_DER)

#Calculate mean differences for all measurements [online]
H1a.2.m_diff <- mean(nonfood2_app$diff_RT) 
H1b.2.m_diff <- mean(nonfood2_app$diff_ER)

H2a.2.m_diff <- mean(food2_app$diff_RT)
H2b.2.m_diff <- mean(food2_app$diff_RT_h)
H2c.2.m_diff <- mean(food2_app$diff_RT_u)
H2d.2.m_diff <- mean(food2_app$diff_DRT)

H3a.2.m_diff <- mean(food2_app$diff_ER)
H3b.2.m_diff <- mean(food2_app$diff_ER_h)
H3c.2.m_diff <- mean(food2_app$diff_ER_u)
H3d.2.m_diff <- mean(food2_app$diff_DER)
```

* Calculate average standard deviation of both measures in t-test comparisons as a standardizer
```{r}
#Calculate average SD for all measures [laboratory]
H1a.1.s_av <- sqrt((H1a.1.sd1^2 + H1a.1.sd2^2)/2)
H1b.1.s_av <- sqrt((H1b.1.sd1^2 + H1b.1.sd2^2)/2)

H2a.1.s_av <- sqrt((H2a.1.sd1^2 + H2a.1.sd2^2)/2)
H2b.1.s_av <- sqrt((H2b.1.sd1^2 + H2b.1.sd2^2)/2)
H2c.1.s_av <- sqrt((H2c.1.sd1^2 + H2c.1.sd2^2)/2)
H2d.1.s_av <- sqrt((H2d.1.sd1^2 + H2d.1.sd2^2)/2)

H3a.1.s_av <- sqrt((H3a.1.sd1^2 + H3a.1.sd2^2)/2)
H3b.1.s_av <- sqrt((H3b.1.sd1^2 + H3b.1.sd2^2)/2)
H3c.1.s_av <- sqrt((H3c.1.sd1^2 + H3c.1.sd2^2)/2)
H3d.1.s_av <- sqrt((H3d.1.sd1^2 + H3d.1.sd2^2)/2)

#Calculate average SD for all measures [online]
H1a.2.s_av <- sqrt((H1a.2.sd1^2 + H1a.2.sd2^2)/2)
H1b.2.s_av <- sqrt((H1b.2.sd1^2 + H1b.2.sd2^2)/2)

H2a.2.s_av <- sqrt((H2a.2.sd1^2 + H2a.2.sd2^2)/2)
H2b.2.s_av <- sqrt((H2b.2.sd1^2 + H2b.2.sd2^2)/2)
H2c.2.s_av <- sqrt((H2c.2.sd1^2 + H2c.2.sd2^2)/2)
H2d.2.s_av <- sqrt((H2d.2.sd1^2 + H2d.2.sd2^2)/2)

H3a.2.s_av <- sqrt((H3a.2.sd1^2 + H3a.2.sd2^2)/2)
H3b.2.s_av <- sqrt((H3b.2.sd1^2 + H3b.2.sd2^2)/2)
H3c.2.s_av <- sqrt((H3c.2.sd1^2 + H3c.2.sd2^2)/2)
H3d.2.s_av <- sqrt((H3d.2.sd1^2 + H3d.2.sd2^2)/2)
```

* Calculate Cohen's dav for all comparisons (H1-H3)

```{r}
#Cohen's dav for H1-H3 [laboratory]
H1a.1.d_av <- H1a.1.m_diff / H1a.1.s_av
H1b.1.d_av <- H1b.1.m_diff / H1b.1.s_av

H2a.1.d_av <- H2a.1.m_diff / H2a.1.s_av
H2b.1.d_av <- H2b.1.m_diff / H2b.1.s_av
H2c.1.d_av <- H2c.1.m_diff / H2c.1.s_av
H2d.1.d_av <- H2d.1.m_diff / H2d.1.s_av

H3a.1.d_av <- H3a.1.m_diff / H3a.1.s_av
H3b.1.d_av <- H3b.1.m_diff / H3b.1.s_av
H3c.1.d_av <- H3c.1.m_diff / H3c.1.s_av
H3d.1.d_av <- H3d.1.m_diff / H3d.1.s_av

#Cohen's dav for H1-H3 [online]
H1a.2.d_av <- H1a.2.m_diff / H1a.2.s_av
H1b.2.d_av <- H1b.2.m_diff / H1b.2.s_av

H2a.2.d_av <- H2a.2.m_diff / H2a.2.s_av
H2b.2.d_av <- H2b.2.m_diff / H2b.2.s_av
H2c.2.d_av <- H2c.2.m_diff / H2c.2.s_av
H2d.2.d_av <- H2d.2.m_diff / H2d.2.s_av

H3a.2.d_av <- H3a.2.m_diff / H3a.2.s_av
H3b.2.d_av <- H3b.2.m_diff / H3b.2.s_av
H3c.2.d_av <- H3c.2.m_diff / H3c.2.s_av
H3d.2.d_av <- H3d.2.m_diff / H3d.2.s_av
```


* Calculate CIs for Cohen's dav
```{r}
#Number of observations
food_N = nrow(food1_app)
nonfood_N = nrow(nonfood1_app)

#Confidence interval
conf_int = 0.95

#T-values from performed t-tests
H1a.1.t_val <- as.numeric(H1a.ST1[[1]]$asDF[4])
H1b.1.t_val <- as.numeric(H1b.ST1[[1]]$asDF[4])

H2a.1.t_val <- as.numeric(H2a.ST1[[1]]$asDF[4])
H2b.1.t_val <- as.numeric(H2b.ST1[[1]]$asDF[4])
H2c.1.t_val <- as.numeric(H2c.ST1[[1]]$asDF[4])
H2d.1.t_val <- as.numeric(H2d.ST1[[1]]$asDF[4])

H3a.1.t_val <- as.numeric(H3a.ST1[[1]]$asDF[4])
H3b.1.t_val <- as.numeric(H3b.ST1[[1]]$asDF[4])
H3c.1.t_val <- as.numeric(H3c.ST1[[1]]$asDF[4])
H3d.1.t_val <- as.numeric(H3d.ST1[[1]]$asDF[4])

H1a.2.t_val <- as.numeric(H1a.ST2[[1]]$asDF[4])
H1b.2.t_val <- as.numeric(H1b.ST2[[1]]$asDF[4])

H2a.2.t_val <- as.numeric(H2a.ST2[[1]]$asDF[4])
H2b.2.t_val <- as.numeric(H2b.ST2[[1]]$asDF[4])
H2c.2.t_val <- as.numeric(H2c.ST2[[1]]$asDF[4])
H2d.2.t_val <- as.numeric(H2d.ST2[[1]]$asDF[4])

H3a.2.t_val <- as.numeric(H3a.ST2[[1]]$asDF[4])
H3b.2.t_val <- as.numeric(H3b.ST2[[1]]$asDF[4])
H3c.2.t_val <- as.numeric(H3c.ST2[[1]]$asDF[4])
H3d.2.t_val <- as.numeric(H3d.ST2[[1]]$asDF[4])

#SDs of the difference scores
H1a.1.s_diff <- sd(nonfood1_app$diff_RT)
H1b.1.s_diff <- sd(nonfood1_app$diff_ER)

H2a.1.s_diff <- sd(food1_app$diff_RT)
H2b.1.s_diff <- sd(food1_app$diff_RT_h)
H2c.1.s_diff <- sd(food1_app$diff_RT_u)
H2d.1.s_diff <- sd(food1_app$diff_DRT)

H3a.1.s_diff <- sd(food1_app$diff_ER)
H3b.1.s_diff <- sd(food1_app$diff_ER_h)
H3c.1.s_diff <- sd(food1_app$diff_ER_u)
H3d.1.s_diff <- sd(food1_app$diff_DER)

H1a.2.s_diff <- sd(nonfood2_app$diff_RT)
H1b.2.s_diff <- sd(nonfood2_app$diff_ER)

H2a.2.s_diff <- sd(food2_app$diff_RT)
H2b.2.s_diff <- sd(food2_app$diff_RT_h)
H2c.2.s_diff <- sd(food2_app$diff_RT_u)
H2d.2.s_diff <- sd(food2_app$diff_DRT)

H3a.2.s_diff <- sd(food2_app$diff_ER)
H3b.2.s_diff <- sd(food2_app$diff_ER_h)
H3c.2.s_diff <- sd(food2_app$diff_ER_u)
H3d.2.s_diff <- sd(food2_app$diff_DER)

#Confidence limits
H1a.1.limits <- conf.limits.nct(t.value = H1a.1.t_val, df=nonfood_N-1, conf.level = conf_int)
H1b.1.limits <- conf.limits.nct(t.value = H1b.1.t_val, df=nonfood_N-1, conf.level = conf_int)

H2a.1.limits <- conf.limits.nct(t.value = H2a.1.t_val, df=food_N-1, conf.level = conf_int)
H2b.1.limits <- conf.limits.nct(t.value = H2b.1.t_val, df=food_N-1, conf.level = conf_int)
H2c.1.limits <- conf.limits.nct(t.value = H2c.1.t_val, df=food_N-1, conf.level = conf_int)
H2d.1.limits <- conf.limits.nct(t.value = H2d.1.t_val, df=food_N-1, conf.level = conf_int)

H3a.1.limits <- conf.limits.nct(t.value = H3a.1.t_val, df=food_N-1, conf.level = conf_int)
H3b.1.limits <- conf.limits.nct(t.value = H3b.1.t_val, df=food_N-1, conf.level = conf_int)
H3c.1.limits <- conf.limits.nct(t.value = H3c.1.t_val, df=food_N-1, conf.level = conf_int)
H3d.1.limits <- conf.limits.nct(t.value = H3d.1.t_val, df=food_N-1, conf.level = conf_int)

H1a.2.limits <- conf.limits.nct(t.value = H1a.2.t_val, df=nonfood_N-1, conf.level = conf_int)
H1b.2.limits <- conf.limits.nct(t.value = H1b.2.t_val, df=nonfood_N-1, conf.level = conf_int)

H2a.2.limits <- conf.limits.nct(t.value = H2a.2.t_val, df=food_N-1, conf.level = conf_int)
H2b.2.limits <- conf.limits.nct(t.value = H2b.2.t_val, df=food_N-1, conf.level = conf_int)
H2c.2.limits <- conf.limits.nct(t.value = H2c.2.t_val, df=food_N-1, conf.level = conf_int)
H2d.2.limits <- conf.limits.nct(t.value = H2d.2.t_val, df=food_N-1, conf.level = conf_int)

H3a.2.limits <- conf.limits.nct(t.value = H3a.2.t_val, df=food_N-1, conf.level = conf_int)
H3b.2.limits <- conf.limits.nct(t.value = H3b.2.t_val, df=food_N-1, conf.level = conf_int)
H3c.2.limits <- conf.limits.nct(t.value = H3c.2.t_val, df=food_N-1, conf.level = conf_int)
H3d.2.limits <- conf.limits.nct(t.value = H3d.2.t_val, df=food_N-1, conf.level = conf_int)

#Lower and upper limits for Cohen's dav
#lci: lower CI
#uci: upper CI

H1a.1.d_av_lci <- H1a.1.limits$Lower.Limit * H1a.1.s_diff / (H1a.1.s_av * sqrt(nonfood_N))
H1a.1.d_av_uci <- H1a.1.limits$Upper.Limit * H1a.1.s_diff / (H1a.1.s_av * sqrt(nonfood_N))

H1b.1.d_av_lci <- H1b.1.limits$Lower.Limit * H1b.1.s_diff / (H1b.1.s_av * sqrt(nonfood_N))
H1b.1.d_av_uci <- H1b.1.limits$Upper.Limit * H1b.1.s_diff / (H1b.1.s_av * sqrt(nonfood_N))

H2a.1.d_av_lci <- H2a.1.limits$Lower.Limit * H2a.1.s_diff / (H2a.1.s_av * sqrt(food_N))
H2a.1.d_av_uci <- H2a.1.limits$Upper.Limit * H2a.1.s_diff / (H2a.1.s_av * sqrt(food_N))

H2b.1.d_av_lci <- H2b.1.limits$Lower.Limit * H2b.1.s_diff / (H2b.1.s_av * sqrt(food_N))
H2b.1.d_av_uci <- H2b.1.limits$Upper.Limit * H2b.1.s_diff / (H2b.1.s_av * sqrt(food_N))

H2c.1.d_av_lci <- H2c.1.limits$Lower.Limit * H2c.1.s_diff / (H2c.1.s_av * sqrt(food_N))
H2c.1.d_av_uci <- H2c.1.limits$Upper.Limit * H2c.1.s_diff / (H2c.1.s_av * sqrt(food_N))

H2d.1.d_av_lci <- H2d.1.limits$Lower.Limit * H2d.1.s_diff / (H2d.1.s_av * sqrt(food_N))
H2d.1.d_av_uci <- H2d.1.limits$Upper.Limit * H2d.1.s_diff / (H2d.1.s_av * sqrt(food_N))

H3a.1.d_av_lci <- H3a.1.limits$Lower.Limit * H3a.1.s_diff / (H3a.1.s_av * sqrt(food_N))
H3a.1.d_av_uci <- H3a.1.limits$Upper.Limit * H3a.1.s_diff / (H3a.1.s_av * sqrt(food_N))

H3b.1.d_av_lci <- H3b.1.limits$Lower.Limit * H3b.1.s_diff / (H3b.1.s_av * sqrt(food_N))
H3b.1.d_av_uci <- H3b.1.limits$Upper.Limit * H3b.1.s_diff / (H3b.1.s_av * sqrt(food_N))

H3c.1.d_av_lci <- H3c.1.limits$Lower.Limit * H3c.1.s_diff / (H3c.1.s_av * sqrt(food_N))
H3c.1.d_av_uci <- H3c.1.limits$Upper.Limit * H3c.1.s_diff / (H3c.1.s_av * sqrt(food_N))

H3d.1.d_av_lci <- H3d.1.limits$Lower.Limit * H3d.1.s_diff / (H3d.1.s_av * sqrt(food_N))
H3d.1.d_av_uci <- H3d.1.limits$Upper.Limit * H3d.1.s_diff / (H3d.1.s_av * sqrt(food_N))


H1a.2.d_av_lci <- H1a.2.limits$Lower.Limit * H1a.2.s_diff / (H1a.2.s_av * sqrt(nonfood_N))
H1a.2.d_av_uci <- H1a.2.limits$Upper.Limit * H1a.2.s_diff / (H1a.2.s_av * sqrt(nonfood_N))

H1b.2.d_av_lci <- H1b.2.limits$Lower.Limit * H1b.2.s_diff / (H1b.2.s_av * sqrt(nonfood_N))
H1b.2.d_av_uci <- H1b.2.limits$Upper.Limit * H1b.2.s_diff / (H1b.2.s_av * sqrt(nonfood_N))

H2a.2.d_av_lci <- H2a.2.limits$Lower.Limit * H2a.2.s_diff / (H2a.2.s_av * sqrt(food_N))
H2a.2.d_av_uci <- H2a.2.limits$Upper.Limit * H2a.2.s_diff / (H2a.2.s_av * sqrt(food_N))

H2b.2.d_av_lci <- H2b.2.limits$Lower.Limit * H2b.2.s_diff / (H2b.2.s_av * sqrt(food_N))
H2b.2.d_av_uci <- H2b.2.limits$Upper.Limit * H2b.2.s_diff / (H2b.2.s_av * sqrt(food_N))

H2c.2.d_av_lci <- H2c.2.limits$Lower.Limit * H2c.2.s_diff / (H2c.2.s_av * sqrt(food_N))
H2c.2.d_av_uci <- H2c.2.limits$Upper.Limit * H2c.2.s_diff / (H2c.2.s_av * sqrt(food_N))

H2d.2.d_av_lci <- H2d.2.limits$Lower.Limit * H2d.2.s_diff / (H2d.2.s_av * sqrt(food_N))
H2d.2.d_av_uci <- H2d.2.limits$Upper.Limit * H2d.2.s_diff / (H2d.2.s_av * sqrt(food_N))

H3a.2.d_av_lci <- H3a.2.limits$Lower.Limit * H3a.2.s_diff / (H3a.2.s_av * sqrt(food_N))
H3a.2.d_av_uci <- H3a.2.limits$Upper.Limit * H3a.2.s_diff / (H3a.2.s_av * sqrt(food_N))

H3b.2.d_av_lci <- H3b.2.limits$Lower.Limit * H3b.2.s_diff / (H3b.2.s_av * sqrt(food_N))
H3b.2.d_av_uci <- H3b.2.limits$Upper.Limit * H3b.2.s_diff / (H3b.2.s_av * sqrt(food_N))

H3c.2.d_av_lci <- H3c.2.limits$Lower.Limit * H3c.2.s_diff / (H3c.2.s_av * sqrt(food_N))
H3c.2.d_av_uci <- H3c.2.limits$Upper.Limit * H3c.2.s_diff / (H3c.2.s_av * sqrt(food_N))

H3d.2.d_av_lci <- H3d.2.limits$Lower.Limit * H3d.2.s_diff / (H3d.2.s_av * sqrt(food_N))
H3d.2.d_av_uci <- H3d.2.limits$Upper.Limit * H3d.2.s_diff / (H3d.2.s_av * sqrt(food_N))
```

* Put all results in a dataframe for reporting purposes

```{r}
effect_sizes <- as.data.frame(matrix(nrow=20, ncol=4))
names(effect_sizes) <- c("Hypothesis", "Cohen's dav", "Lower CI", "Upper CI")

effect_sizes$Hypothesis <- c("H1a.1", "H1b.1", "H2a.1", "H2b.1", "H2c.1", "H2d.1", "H3a.1", "H3b.1","H3c.1", "H3d.1",
                             "H1a.2", "H1b.2", "H2a.2", "H2b.2", "H2c.2", "H2d.2", "H3a.2", "H3b.2","H3c.2", "H3d.2")

effect_sizes$`Cohen's dav` <- c(H1a.1.d_av, H1b.1.d_av, H2a.1.d_av, H2b.1.d_av, H2c.1.d_av, H2d.1.d_av,
                               H3a.1.d_av, H3b.1.d_av, H3c.1.d_av, H3d.1.d_av,
                               H1a.2.d_av, H1b.2.d_av, H2a.2.d_av, H2b.2.d_av, H2c.2.d_av, H2d.2.d_av,
                               H3a.2.d_av, H3b.2.d_av, H3c.2.d_av, H3d.2.d_av)

effect_sizes$`Lower CI` <- c(H1a.1.d_av_lci, H1b.1.d_av_lci, H2a.1.d_av_lci, H2b.1.d_av_lci, H2c.1.d_av_lci, H2d.1.d_av_lci,
                             H3a.1.d_av_lci, H3b.1.d_av_lci, H3c.1.d_av_lci, H3d.1.d_av_lci,
                             H1a.2.d_av_lci, H1b.2.d_av_lci, H2a.2.d_av_lci, H2b.2.d_av_lci, H2c.2.d_av_lci, H2d.2.d_av_lci,
                             H3a.2.d_av_lci, H3b.2.d_av_lci, H3c.2.d_av_lci, H3d.2.d_av_lci)

effect_sizes$`Upper CI` <- c(H1a.1.d_av_uci, H1b.1.d_av_uci, H2a.1.d_av_uci, H2b.1.d_av_uci, H2c.1.d_av_uci, H2d.1.d_av_uci,
                             H3a.1.d_av_uci, H3b.1.d_av_uci, H3c.1.d_av_uci, H3d.1.d_av_uci,
                             H1a.2.d_av_uci, H1b.2.d_av_uci, H2a.2.d_av_uci, H2b.2.d_av_uci, H2c.2.d_av_uci, H2d.2.d_av_uci,
                             H3a.2.d_av_uci, H3b.2.d_av_uci, H3c.2.d_av_uci, H3d.2.d_av_uci)
```
