---
title: "3. Robustness checks"
author: "Loukia Tzavella"
date: "29/01/2019"
output: html_document
---

#### Robustness checks

> The pre-registered hypotheses of the study will be tested under different data aggregation and reduction conditions. 
> Following the sensitivity analyses, we can conclude that the findings of the study are 'robust' if the results are consistent with those of the main pre-registered analyses in the manuscript. 
> We use the initial 'S' to refer to sensitivity analyses across this script (e.g., "food1_app_S").
> Outlier removal criteria have been adopted from previous literature, as cited in the manuscript. 

#### Mean instead of median RTs at the participant level and outlier exclusion criteria

* Prepare data for 'trimr' functions  that removes outliers based on absolute values and/or SDs
* The package requires that certain data columns are named exaclty as shown below:
  participant, condition, rt, accuracy 

* Change structure of datalists with correct RTs only

```{r}
# Our data column names are consistent with the trimr package except for 'condition'

# To capture each cell of the design we will use the variable 'trial'
# which contains the unique trialcodes and save a copy in a factor format

food1_cor <- lapply(food1_cor, transform, condition = as.factor(trial))
food2_cor <- lapply(food2_cor, transform, condition = as.factor(trial))

nonfood1_cor <- lapply(nonfood1_cor, transform, condition = as.factor(trial))
nonfood2_cor <- lapply(nonfood2_cor, transform, condition = as.factor(trial))
```

* Apply error rate exclusions 

```{r}
# Exclude participants who had mean error rates > 0.4

food1_cor <- food1_cor[sapply(food1_cor, function(x) any(!x$participant %in% ER1_excl))]
food2_cor <- food2_cor[sapply(food2_cor, function(x) any(!x$participant %in% ER2_excl))]

nonfood1_cor <- nonfood1_cor[sapply(nonfood1_cor, function(x) any(!x$participant %in% ER1_excl))]
nonfood2_cor <- nonfood2_cor[sapply(nonfood2_cor, function(x) any(!x$participant %in% ER2_excl))]
```


* Outlier exclusion 1: Remove RTs <250 ms

```{r}
# First we record the number of trials that meet the criterion to manually check whether
# how much data would be removed for each participant and how many participants in total
food1_cor <- lapply(food1_cor, transform, MinRT = ifelse(rt < 250, 1, 0))
minRTs1 <- ldply(food1_cor, function(x) nrow(subset(x, MinRT == 1)))

table(minRTs1$V1)

# We repeat this procedure for online data and non-food data from both cohorts
food2_cor <- lapply(food2_cor, transform, MinRT = ifelse(rt < 250, 1, 0))
minRTs2 <- ldply(food2_cor, function(x) nrow(subset(x, MinRT == 1)))

table(minRTs2$V1)


nonfood1_cor <- lapply(nonfood1_cor, transform, MinRT = ifelse(rt < 250, 1, 0))
minRTs1b <- ldply(nonfood1_cor, function(x) nrow(subset(x, MinRT == 1)))

table(minRTs1b$V1)


nonfood2_cor <- lapply(nonfood2_cor, transform, MinRT = ifelse(rt < 250, 1, 0))
minRTs2b <- ldply(nonfood2_cor, function(x) nrow(subset(x, MinRT == 1)))

table(minRTs2b$V1)
```


```{r}
# Apply RT exclusion for <250ms criterion
food1_RT1 <- lapply(food1_cor, function(x) x <- absoluteRT(x, minRT = 250, maxRT = 1500, returnType = "raw", omitErrors = FALSE))
food2_RT1 <- lapply(food2_cor, function(x) x <- absoluteRT(x, minRT = 250, maxRT = 1500, returnType = "raw", omitErrors = FALSE))

nonfood1_RT1 <- lapply(nonfood1_cor, function(x) x <- absoluteRT(x, minRT = 250, maxRT = 1500, returnType = "raw", omitErrors = FALSE))
nonfood2_RT1 <- lapply(nonfood2_cor, function(x) x <- absoluteRT(x, minRT = 250, maxRT = 1500, returnType = "raw", omitErrors = FALSE))
```


* Outlier exclusion 2: Remove RTs >2.5 SDs from the mean of each design cell

```{r}
# perParticipant would normally be set to TRUE, but for a list of dataframes from individual participants this is not needed.

food1_RT2 <- lapply(food1_cor, function(x) x <- sdTrim(x, minRT = 0, sd = 2.5, perCondition = TRUE, perParticipant = FALSE, returnType = "raw", omitErrors = FALSE))
food2_RT2 <- lapply(food2_cor, function(x) x <- sdTrim(x, minRT = 0, sd = 2.5, perCondition = TRUE, perParticipant = FALSE, returnType = "raw", omitErrors = FALSE))

nonfood1_RT2 <- lapply(nonfood1_cor, function(x) x <- sdTrim(x, minRT = 0, sd = 2.5, perCondition = TRUE, perParticipant = FALSE, returnType = "raw", omitErrors = FALSE))
nonfood2_RT2 <- lapply(nonfood2_cor, function(x) x <- sdTrim(x, minRT = 0, sd = 2.5, perCondition = TRUE, perParticipant = FALSE, returnType = "raw", omitErrors = FALSE))

# Get number of trials that were removed from the data

food1_RT2rm <- cbind(ldply(food1_cor, function(x) nrow(x)), ldply(food1_RT2, function(x) nrow(x)))
food1_RT2rm$ntrials <- food1_RT2rm[2] - food1_RT2rm[4]

food2_RT2rm <- cbind(ldply(food2_cor, function(x) nrow(x)), ldply(food2_RT2, function(x) nrow(x)))
food2_RT2rm$ntrials <- food2_RT2rm[2] - food2_RT2rm[4]

nonfood1_RT2rm <- cbind(ldply(nonfood1_cor, function(x) nrow(x)), ldply(nonfood1_RT2, function(x) nrow(x)))
nonfood1_RT2rm$ntrials <- nonfood1_RT2rm[2] - nonfood1_RT2rm[4]

nonfood2_RT2rm <- cbind(ldply(nonfood2_cor, function(x) nrow(x)), ldply(nonfood2_RT2, function(x) nrow(x)))
nonfood2_RT2rm$ntrials <- nonfood2_RT2rm[2] - nonfood2_RT2rm[4]
```

* Create dataframes with mean instead of median RTs for analyses

```{r}
# Mean RTs of correct trials from non-food trials
nonfood1_RT1 <- ldply(nonfood1_RT1, NF_means)
nonfood2_RT1 <- ldply(nonfood2_RT1, NF_means)

nonfood1_RT2 <- ldply(nonfood1_RT2, NF_means)
nonfood2_RT2 <- ldply(nonfood2_RT2, NF_means)

# Mean RTs of correct trials from food trials
food1_RT1 <- ldply(food1_RT1, F_means)
food2_RT1 <- ldply(food2_RT1, F_means)

food1_RT2 <- ldply(food1_RT2, F_means)
food2_RT2 <- ldply(food2_RT2, F_means)
```

* Calculate priming effects for confirmatory analyses

```{r}
# Lab data - RT1
food1_RT1$DRT_h <- food1_RT1$inc_hml_RT - food1_RT1$con_hml_RT
food1_RT1$DRT_u <- food1_RT1$inc_uml_RT - food1_RT1$con_uml_RT

food1_RT1$DRT_hml <- food1_RT1$DRT_u - food1_RT1$DRT_h

# Online data - RT1
food2_RT1$DRT_h <- food2_RT1$inc_hml_RT - food2_RT1$con_hml_RT
food2_RT1$DRT_u <- food2_RT1$inc_uml_RT - food2_RT1$con_uml_RT

food2_RT1$DRT_hml <- food2_RT1$DRT_u - food2_RT1$DRT_h

# Lab data - RT2
food1_RT2$DRT_h <- food1_RT2$inc_hml_RT - food1_RT2$con_hml_RT
food1_RT2$DRT_u <- food1_RT2$inc_uml_RT - food1_RT2$con_uml_RT

food1_RT2$DRT_hml <- food1_RT2$DRT_u - food1_RT2$DRT_h

# Online data - RT2
food2_RT2$DRT_h <- food2_RT2$inc_hml_RT - food2_RT2$con_hml_RT
food2_RT2$DRT_u <- food2_RT2$inc_uml_RT - food2_RT2$con_uml_RT

food2_RT2$DRT_hml <- food2_RT2$DRT_u - food2_RT2$DRT_h
```

* Obtain difference scores for effect size calculation and normality tests

```{r}
# Lab data - RT1
food1_RT1$diff_RT <- food1_RT1$con_RT - food1_RT1$inc_RT
food1_RT1$diff_RT_h <- food1_RT1$con_h_RT - food1_RT1$inc_h_RT
food1_RT1$diff_RT_u <- food1_RT1$con_u_RT - food1_RT1$inc_u_RT
food1_RT1$diff_DRT <- food1_RT1$DRT_h - food1_RT1$DRT_u

nonfood1_RT1$diff_RT <- nonfood1_RT1$con_RT - nonfood1_RT1$inc_RT

# Online data - RT1
food2_RT1$diff_RT <- food2_RT1$con_RT - food2_RT1$inc_RT
food2_RT1$diff_RT_h <- food2_RT1$con_h_RT - food2_RT1$inc_h_RT
food2_RT1$diff_RT_u <- food2_RT1$con_u_RT - food2_RT1$inc_u_RT
food2_RT1$diff_DRT <- food2_RT1$DRT_h - food2_RT1$DRT_u

nonfood2_RT1$diff_RT <- nonfood2_RT1$con_RT - nonfood2_RT1$inc_RT

# Lab data - RT2
food1_RT2$diff_RT <- food1_RT2$con_RT - food1_RT2$inc_RT
food1_RT2$diff_RT_h <- food1_RT2$con_h_RT - food1_RT2$inc_h_RT
food1_RT2$diff_RT_u <- food1_RT2$con_u_RT - food1_RT2$inc_u_RT
food1_RT2$diff_DRT <- food1_RT2$DRT_h - food1_RT2$DRT_u

nonfood1_RT2$diff_RT <- nonfood1_RT2$con_RT - nonfood1_RT2$inc_RT

# Online data - RT2
food2_RT2$diff_RT <- food2_RT2$con_RT - food2_RT2$inc_RT
food2_RT2$diff_RT_h <- food2_RT2$con_h_RT - food2_RT2$inc_h_RT
food2_RT2$diff_RT_u <- food2_RT2$con_u_RT - food2_RT2$inc_u_RT
food2_RT2$diff_DRT <- food2_RT2$DRT_h - food2_RT2$DRT_u

nonfood2_RT2$diff_RT <- nonfood2_RT2$con_RT - nonfood2_RT2$inc_RT
```

*Check new datasets for violation of the normality assumption 

```{r message=FALSE}
# Re-run Shapiro-Wilk tests for RTs (H1a, H2a-H2d)
SW_RT_S1a <- Shapiro_wilk_RTs(food1_RT1, nonfood1_RT1)
SW_RT_S1b <- Shapiro_wilk_RTs(food2_RT1, nonfood2_RT1)

SW_RT_S2a <- Shapiro_wilk_RTs(food1_RT2, nonfood1_RT2)
SW_RT_S2b <- Shapiro_wilk_RTs(food2_RT2, nonfood2_RT2)

# Log-transform RTs if normality assumption is violated
food1_RT1 <- log_H2R(data = food1_RT1, sw = SW_RT_S1a)
food2_RT1 <- log_H2R(data = food2_RT1, sw = SW_RT_S1b)

food1_RT2 <- log_H2R(data = food1_RT2, sw = SW_RT_S2a)
food2_RT2 <- log_H2R(data = food2_RT2, sw = SW_RT_S2b)

nonfood1_RT1 <- log_H1R(data = nonfood1_RT1, sw = SW_RT_S1a)
nonfood2_RT1 <- log_H1R(data = nonfood2_RT1, sw = SW_RT_S1b)

nonfood1_RT2 <- log_H1R(data = nonfood1_RT2, sw = SW_RT_S2a)
nonfood2_RT2 <- log_H1R(data = nonfood2_RT2, sw = SW_RT_S2b)

# If RTs are log transformed we will need to recalculate the difference scores

food1_RT1 <- log_diff(food1_RT1)
food1_RT2 <- log_diff(food1_RT2)

food2_RT1 <- log_diff(food2_RT1)
food2_RT2 <- log_diff(food2_RT2)
```

* Merge new datasets with FCT outcomes

```{r}
# Re-apply exclusions for missed responses to APP data
# Note. These are not affected by, or related to, any RT removal criteria

FCT_app1_S1 <- subset(food1_RT1, select = c(".id", "DRT_h", "DRT_u", "DRT_hml"))
FCT_app1_S1 <- subset(FCT_app1_S1, .id %in% FCT1_incl)

FCT_app2_S1 <- subset(food2_RT1, select = c(".id", "DRT_h", "DRT_u", "DRT_hml"))
FCT_app2_S1 <- subset(FCT_app2_S1, .id %in% FCT2_incl)

FCT_app1_S2 <- subset(food1_RT2, select = c(".id", "DRT_h", "DRT_u", "DRT_hml"))
FCT_app1_S2 <- subset(FCT_app1_S2, .id %in% FCT1_incl)

FCT_app2_S2 <- subset(food2_RT2, select = c(".id", "DRT_h", "DRT_u", "DRT_hml"))
FCT_app2_S2 <- subset(FCT_app2_S2, .id %in% FCT2_incl)

# Merge APP and FCT data
FCT_full1_S1 <- cbind(FCT_app1_S1, FCT1_outcomes)
FCT_full2_S1 <- cbind(FCT_app2_S1, FCT2_outcomes)

FCT_full1_S2 <- cbind(FCT_app1_S2, FCT1_outcomes)
FCT_full2_S2 <- cbind(FCT_app2_S2, FCT2_outcomes)
```

* Re-run analyses for RT-related hypotheses

> Laboratory data - RT criterion 1 

```{r message=FALSE, warning=FALSE}
if (nonfood1_app$transform == "none") {
  H1a.BF1_S1 <- ttestBF(x = nonfood1_RT1$con_RT, y = nonfood1_RT1$inc_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H1a.BF1_S1 <- ttestBF(x = nonfood1_RT1$logRTcon, y = nonfood1_RT1$logRTinc, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r}
H1a.BF1_S1
```

```{r message=FALSE, warning=FALSE}
if (food1_RT1$transform == "none") {
  H2a.BF1_S1 <- ttestBF(x = food1_RT1$con_RT, y = food1_RT1$inc_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2a.BF1_S1 <- ttestBF(x = food1_RT1$logRTcon, y = food1_RT1$logRTinc, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```
```{r message=FALSE, warning=FALSE}
if (food1_RT1$transform == "none") {
  H2b.BF1_S1 <- ttestBF(x = food1_RT1$con_h_RT, y = food1_RT1$inc_h_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2b.BF1_S1 <- ttestBF(x = food1_RT1$logRTcon_h, y = food1_RT1$logRTinc_h, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```
```{r message=FALSE, warning=FALSE}
if (food1_RT1$transform == "none") {
  H2c.BF1_S1 <- ttestBF(x = food1_RT1$con_u_RT, y = food1_RT1$inc_u_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2c.BF1_S1 <- ttestBF(x = food1_RT1$logRTcon_u, y = food1_RT1$logRTinc_u, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r message=FALSE, warning=FALSE}
if (food1_RT1$transform == "none") {
  H2d.BF1_S1 <- ttestBF(x = food1_RT1$DRT_h, y = food1_RT1$DRT_u, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2d.BF1_S1 <- ttestBF(x = food1_RT1$DRT_h_log, y = food1_RT1$DRT_u_log, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r}
H2a.BF1_S1
```

```{r}
H2b.BF1_S1
```

```{r}
H2c.BF1_S1
```

```{r}
H2d.BF1_S1
```

```{r}
# Bayesian correlation pairs for H4 [food choices]
H4a.BF1_S1 <- correlationBF(x = FCT_full1_S1$DRT_h, y = FCT_full1_S1$p.mh, rscale = 1, nullInterval = c(0, 1))

H4b.BF1_S1 <- correlationBF(x = FCT_full1_S1$DRT_u, y = FCT_full1_S1$p.mu, rscale = 1, nullInterval = c(0, 1))

H4c.BF1_S1 <- correlationBF(x = FCT_full1_S1$DRT_hml, y = FCT_full1_S1$p.um, rscale = 1, nullInterval = c(0, 1))
```

```{r}
H4a.BF1_S1
```

```{r}
H4b.BF1_S1
```

```{r}
H4c.BF1_S1
```

> Laboratory data - RT criterion 2

```{r message=FALSE, warning=FALSE}
if (nonfood1_app$transform == "none") {
  H1a.BF1_S2 <- ttestBF(x = nonfood1_RT2$con_RT, y = nonfood1_RT2$inc_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H1a.BF1_S2 <- ttestBF(x = nonfood1_RT2$logRTcon, y = nonfood1_RT2$logRTinc, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r}
H1a.BF1_S2
```

```{r message=FALSE, warning=FALSE}
if (food1_RT1$transform == "none") {
  H2a.BF1_S2 <- ttestBF(x = food1_RT2$con_RT, y = food1_RT2$inc_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2a.BF1_S2 <- ttestBF(x = food1_RT2$logRTcon, y = food1_RT2$logRTinc, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r message=FALSE, warning=FALSE}
if (food1_RT1$transform == "none") {
  H2b.BF1_S2 <- ttestBF(x = food1_RT2$con_h_RT, y = food1_RT2$inc_h_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2b.BF1_S2 <- ttestBF(x = food1_RT2$logRTcon_h, y = food1_RT2$logRTinc_h, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r message=FALSE, warning=FALSE}
if (food1_RT1$transform == "none") {
  H2c.BF1_S2 <- ttestBF(x = food1_RT2$con_u_RT, y = food1_RT2$inc_u_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2c.BF1_S2 <- ttestBF(x = food1_RT2$logRTcon_u, y = food1_RT2$logRTinc_u, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r message=FALSE, warning=FALSE}
if (food1_RT1$transform == "none") {
  H2d.BF1_S2 <- ttestBF(x = food1_RT2$DRT_h, y = food1_RT2$DRT_u, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2d.BF1_S2 <- ttestBF(x = food1_RT2$DRT_h_log, y = food1_RT2$DRT_u_log, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r}
H2a.BF1_S2
```

```{r}
H2b.BF1_S2
```

```{r}
H2c.BF1_S2
```

```{r}
H2d.BF1_S2
```


```{r}
H4a.BF1_S2 <- correlationBF(x = FCT_full1_S2$DRT_h, y = FCT_full1_S2$p.mh, rscale = 1, nullInterval = c(0, 1))
H4b.BF1_S2 <- correlationBF(x = FCT_full1_S2$DRT_u, y = FCT_full1_S2$p.mu, rscale = 1, nullInterval = c(0, 1))
H4c.BF1_S2 <- correlationBF(x = FCT_full1_S2$DRT_hml, y = FCT_full1_S2$p.um, rscale = 1, nullInterval = c(0, 1))
```


```{r}
H4a.BF1_S2
```

```{r}
H4b.BF1_S2
```

```{r}
H4c.BF1_S2
```

> Online data - RT criterion 1 

```{r message=FALSE, warning=FALSE}
if (nonfood2_app$transform == "none") {
  H1a.BF2_S1 <- ttestBF(x = nonfood2_RT1$con_RT, y = nonfood2_RT1$inc_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H1a.BF2_S1 <- ttestBF(x = nonfood2_RT1$logRTcon, y = nonfood2_RT1$logRTinc, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r}
H1a.BF2_S1
```

```{r message=FALSE, warning=FALSE}
if (food2_RT1$transform == "none") {
  H2a.BF2_S1 <- ttestBF(x = food2_RT1$con_RT, y = food2_RT1$inc_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2a.BF2_S1 <- ttestBF(x = food2_RT1$logRTcon, y = food2_RT1$logRTinc, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```
```{r message=FALSE, warning=FALSE}
if (food2_RT1$transform == "none") {
  H2b.BF2_S1 <- ttestBF(x = food2_RT1$con_h_RT, y = food2_RT1$inc_h_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2b.BF2_S1 <- ttestBF(x = food2_RT1$logRTcon_h, y = food2_RT1$logRTinc_h, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```
```{r message=FALSE, warning=FALSE}
if (food2_RT1$transform == "none") {
  H2c.BF2_S1 <- ttestBF(x = food2_RT1$con_u_RT, y = food2_RT1$inc_u_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2c.BF2_S1 <- ttestBF(x = food2_RT1$logRTcon_u, y = food2_RT1$logRTinc_u, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r message=FALSE, warning=FALSE}
if (food2_RT1$transform == "none") {
  H2d.BF2_S1 <- ttestBF(x = food2_RT1$DRT_h, y = food2_RT1$DRT_u, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2d.BF2_S1 <- ttestBF(x = food2_RT1$DRT_h_log, y = food2_RT1$DRT_u_log, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r}
H2a.BF2_S1
```

```{r}
H2b.BF2_S1
```

```{r}
H2c.BF2_S1
```

```{r}
H2d.BF2_S1
```

```{r}
# Bayesian correlation pairs for H4 [food choices]
H4a.BF2_S1 <- correlationBF(x = FCT_full2_S1$DRT_h, y = FCT_full2_S1$p.mh, rscale = 1, nullInterval = c(0, 1))

H4b.BF2_S1 <- correlationBF(x = FCT_full2_S1$DRT_u, y = FCT_full2_S1$p.mu, rscale = 1, nullInterval = c(0, 1))

H4c.BF2_S1 <- correlationBF(x = FCT_full2_S1$DRT_hml, y = FCT_full2_S1$p.um, rscale = 1, nullInterval = c(0, 1))
```

```{r}
H4a.BF2_S1
```

```{r}
H4b.BF2_S1
```

```{r}
H4c.BF2_S1
```

> Online data - RT criterion 2

```{r message=FALSE, warning=FALSE}
if (nonfood2_app$transform == "none") {
  H1a.BF2_S2 <- ttestBF(x = nonfood2_RT2$con_RT, y = nonfood2_RT2$inc_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H1a.BF2_S2 <- ttestBF(x = nonfood2_RT2$logRTcon, y = nonfood2_RT2$logRTinc, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r}
H1a.BF2_S2
```

```{r message=FALSE, warning=FALSE}
if (food2_RT1$transform == "none") {
  H2a.BF2_S2 <- ttestBF(x = food2_RT2$con_RT, y = food2_RT2$inc_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2a.BF2_S2 <- ttestBF(x = food2_RT2$logRTcon, y = food2_RT2$logRTinc, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r message=FALSE, warning=FALSE}
if (food2_RT1$transform == "none") {
  H2b.BF2_S2 <- ttestBF(x = food2_RT2$con_h_RT, y = food2_RT2$inc_h_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2b.BF2_S2 <- ttestBF(x = food2_RT2$logRTcon_h, y = food2_RT2$logRTinc_h, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r message=FALSE, warning=FALSE}
if (food2_RT1$transform == "none") {
  H2c.BF2_S2 <- ttestBF(x = food2_RT2$con_u_RT, y = food2_RT2$inc_u_RT, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2c.BF2_S2 <- ttestBF(x = food2_RT2$logRTcon_u, y = food2_RT2$logRTinc_u, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r message=FALSE, warning=FALSE}
if (food2_RT1$transform == "none") {
  H2d.BF2_S2 <- ttestBF(x = food2_RT2$DRT_h, y = food2_RT2$DRT_u, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("non-transformed")
} else {
  H2d.BF2_S2 <- ttestBF(x = food2_RT2$DRT_h_log, y = food2_RT2$DRT_u_log, paired = TRUE, rscale = "medium", nullInterval = c(-Inf, 0))
  print("log-transformed")
}
```

```{r}
H2a.BF2_S2
```

```{r}
H2b.BF2_S2
```

```{r}
H2c.BF2_S2
```

```{r}
H2d.BF2_S2
```


```{r}
H4a.BF2_S2 <- correlationBF(x = FCT_full2_S2$DRT_h, y = FCT_full2_S2$p.mh, rscale = 1, nullInterval = c(0, 1))
H4b.BF2_S2 <- correlationBF(x = FCT_full2_S2$DRT_u, y = FCT_full2_S2$p.mu, rscale = 1, nullInterval = c(0, 1))
H4c.BF2_S2 <- correlationBF(x = FCT_full2_S2$DRT_hml, y = FCT_full2_S2$p.um, rscale = 1, nullInterval = c(0, 1))
```


```{r}
H4a.BF2_S2
```

```{r}
H4b.BF2_S2
```

```{r}
H4c.BF2_S2
```

* Save all results in a table for exported csv

```{r}
robust1 <- data.frame(matrix(ncol = 3, nrow = 8))
names(robust1) <- c("Hypothesis", "logBF10_1", "logBF10_2")

robust1$Hypothesis <- c("H1a", "H2a", "H2b", "H2c", "H2d", "H4a", "H4b", "H4c")

robust1$logBF10_1[1] <- H1a.BF1_S1@bayesFactor[1, 1]
robust1$logBF10_1[2] <- H2a.BF1_S1@bayesFactor[1, 1]
robust1$logBF10_1[3] <- H2b.BF1_S1@bayesFactor[1, 1]
robust1$logBF10_1[4] <- H2c.BF1_S1@bayesFactor[1, 1]
robust1$logBF10_1[5] <- H2d.BF1_S1@bayesFactor[1, 1]
robust1$logBF10_1[6] <- H4a.BF1_S1@bayesFactor[1, 1]
robust1$logBF10_1[7] <- H4b.BF1_S1@bayesFactor[1, 1]
robust1$logBF10_1[8] <- H4c.BF1_S1@bayesFactor[1, 1]

robust1$logBF10_2[1] <- H1a.BF1_S2@bayesFactor[1, 1]
robust1$logBF10_2[2] <- H2a.BF1_S2@bayesFactor[1, 1]
robust1$logBF10_2[3] <- H2b.BF1_S2@bayesFactor[1, 1]
robust1$logBF10_2[4] <- H2c.BF1_S2@bayesFactor[1, 1]
robust1$logBF10_2[5] <- H2d.BF1_S2@bayesFactor[1, 1]
robust1$logBF10_2[6] <- H4a.BF1_S2@bayesFactor[1, 1]
robust1$logBF10_2[7] <- H4b.BF1_S2@bayesFactor[1, 1]
robust1$logBF10_2[8] <- H4c.BF1_S2@bayesFactor[1, 1]

robust2 <- data.frame(matrix(ncol = 3, nrow = 8))
names(robust2) <- c("Hypothesis", "logBF10_1", "logBF10_2")

robust2$Hypothesis <- c("H1a", "H2a", "H2b", "H2c", "H2d", "H4a", "H4b", "H4c")

robust2$logBF10_1[1] <- H1a.BF2_S1@bayesFactor[1, 1]
robust2$logBF10_1[2] <- H2a.BF2_S1@bayesFactor[1, 1]
robust2$logBF10_1[3] <- H2b.BF2_S1@bayesFactor[1, 1]
robust2$logBF10_1[4] <- H2c.BF2_S1@bayesFactor[1, 1]
robust2$logBF10_1[5] <- H2d.BF2_S1@bayesFactor[1, 1]
robust2$logBF10_1[6] <- H4a.BF2_S1@bayesFactor[1, 1]
robust2$logBF10_1[7] <- H4b.BF2_S1@bayesFactor[1, 1]
robust2$logBF10_1[8] <- H4c.BF2_S1@bayesFactor[1, 1]

robust2$logBF10_2[1] <- H1a.BF2_S2@bayesFactor[1, 1]
robust2$logBF10_2[2] <- H2a.BF2_S2@bayesFactor[1, 1]
robust2$logBF10_2[3] <- H2b.BF2_S2@bayesFactor[1, 1]
robust2$logBF10_2[4] <- H2c.BF2_S2@bayesFactor[1, 1]
robust2$logBF10_2[5] <- H2d.BF2_S2@bayesFactor[1, 1]
robust2$logBF10_2[6] <- H4a.BF2_S2@bayesFactor[1, 1]
robust2$logBF10_2[7] <- H4b.BF2_S2@bayesFactor[1, 1]
robust2$logBF10_2[8] <- H4c.BF2_S2@bayesFactor[1, 1]

write.csv(robust1, "robust1.csv", row.names = FALSE)
write.csv(robust2, "robust2.csv", row.names = FALSE)
```

