---
title: "BFDA script"
author: "Loukia Tzavella"
date: "21/08/2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = 'hide')
```

#### Install and/or load required packages
```{r}
required <- c("devtools", "BFDA", "ggplot2")
new <- required[!(required %in% installed.packages()[,"Package"])]

if("devtools" %in% new) {install.packages("devtools")}
if("BFDA" %in% new) {install_github("nicebread/BFDA", subdir="package")}

require(devtools)
require(BFDA)
require(ggplot2)
```

## Simulation parameters for Bayesian paired-samples t-tests:

* n.min = 40 [minimum number of participants]
* n.max = 200 [maximum number of participants]
* expected.ES = 0, 0.2, 0.5,0.8 [Cohen's dz] 
* Sequential design for paired t-test (directional)
* Default prior of r = sqrt(2)/2
* boundary = 10 [BF~10~>=10 for H1 and BF~0~>=10, or BF~10~<=1/10, for H0]
* stepsize = 10 [analyses conducted for every 10 participants]
* B = 10000 [number of bootstrap samples]

#### Create a dataframe for storing simulation results later in the script

```{r}
data <- as.data.frame(matrix(ncol=3, nrow=10))   
names(data) <- c("Sample_size", "Boundary", "Percentage")

data$Boundary <- c(rep("H1",times=5), rep("H0",times=5))
data$Sample_size <- c(40,80,120,160,200,40,80,120,160,200)
data$Boundary <- as.factor(data$Boundary)
```

#### Simulation for H0 (Cohen's dz=0) and BFDA results

```{r}
sim.H0 <- BFDA.sim(expected.ES = 0, type="t.paired", n.min=40, n.max=200,  r=sqrt(2)/2, alternative="directional", B=10000, verbose=TRUE, cores=4, stepsize=10,  design="sequential") 
```

```{r}
# Bayes Factor Design Analyses for selected sample sizes

res1.H0 <- BFDA.analyze(sim.H0, design="sequential", n.max=40, boundary=10)
res2.H0 <- BFDA.analyze(sim.H0, design="sequential", n.max=80, boundary=10)
res3.H0 <- BFDA.analyze(sim.H0, design="sequential", n.max=120, boundary=10)
res4.H0 <- BFDA.analyze(sim.H0, design="sequential", n.max=160, boundary=10)
res5.H0 <- BFDA.analyze(sim.H0, design="sequential", n.max=200, boundary=10)
```

```{r}
# Saving analysis results of interest in named variables for later inclusion in a complete dataframe

# % studies terminating at H1 boundary (upper.hit.frac) and % studies terminating at H0 boundary      (lower.hit.frac)

# Results from each analysis can be seen in detail with the relevant R objects (e.g., res1.H0)

H0_1<- res1.H0$upper.hit.frac*100
H0_1n <- res1.H0$lower.hit.frac*100

H0_2 <- res2.H0$upper.hit.frac*100
H0_2n <- res2.H0$lower.hit.frac*100

H0_3 <- res3.H0$upper.hit.frac*100
H0_3n <- res3.H0$lower.hit.frac*100

H0_4 <- res4.H0$upper.hit.frac*100
H0_4n <- res4.H0$lower.hit.frac*100

H0_5 <- res5.H0$upper.hit.frac*100
H0_5n <- res5.H0$lower.hit.frac*100
```

```{r}
#Store all results in a dataframe for plotting purposes

H0_data <- data
H0_data$Percentage <- c(H0_1,H0_2,H0_3,H0_4,H0_5,H0_1n,H0_2n,H0_3n,H0_4n,H0_5n)
```

#### Simulation for H1 (Cohen's dz=0.2) and BFDA results

```{r}
sim.H1a <- BFDA.sim(expected.ES = 0.2, type="t.paired", n.min=40, n.max=200,  r=sqrt(2)/2, alternative="directional", B=10000, verbose=TRUE, cores=4, stepsize=10, design = "sequential") 
```

```{r}
res1.H1a <- BFDA.analyze(sim.H1a, design="sequential", n.max=40, boundary=10)
res2.H1a <- BFDA.analyze(sim.H1a, design="sequential", n.max=80, boundary=10)
res3.H1a <- BFDA.analyze(sim.H1a, design="sequential", n.max=120, boundary=10)
res4.H1a <- BFDA.analyze(sim.H1a, design="sequential", n.max=160, boundary=10)
res5.H1a <- BFDA.analyze(sim.H1a, design="sequential", n.max=200, boundary=10)
```

```{r}
H1a_1<- res1.H1a$upper.hit.frac*100
H1a_1n <- res1.H1a$lower.hit.frac*100

H1a_2 <- res2.H1a$upper.hit.frac*100
H1a_2n <- res2.H1a$lower.hit.frac*100

H1a_3 <- res3.H1a$upper.hit.frac*100
H1a_3n <- res3.H1a$lower.hit.frac*100

H1a_4 <- res4.H1a$upper.hit.frac*100
H1a_4n <- res4.H1a$lower.hit.frac*100

H1a_5 <- res5.H1a$upper.hit.frac*100
H1a_5n <- res5.H1a$lower.hit.frac*100
```

```{r}
H1a_data <- data
H1a_data$Percentage <- c(H1a_1,H1a_2,H1a_3,H1a_4,H1a_5,H1a_1n,H1a_2n,H1a_3n,H1a_4n,H1a_5n)
```

#### Simulation for H1 (Cohen's dz=0.5) and BFDA results 

```{r}
sim.H1b <- BFDA.sim(expected.ES = 0.5, type="t.paired", n.min=40, n.max=200,  r=sqrt(2)/2, alternative="directional", B=10000, verbose=TRUE, cores=4, stepsize=10, design = "sequential") 
```

```{r}
res1.H1b <- BFDA.analyze(sim.H1b, design="sequential", n.max=40, boundary=10)
res2.H1b <- BFDA.analyze(sim.H1b, design="sequential", n.max=80, boundary=10)
res3.H1b <- BFDA.analyze(sim.H1b, design="sequential", n.max=120, boundary=10)
res4.H1b <- BFDA.analyze(sim.H1b, design="sequential", n.max=160, boundary=10)
res5.H1b <- BFDA.analyze(sim.H1b, design="sequential", n.max=200, boundary=10)
```

```{r}
H1b_1<- res1.H1b$upper.hit.frac*100
H1b_1n <- res1.H1b$lower.hit.frac*100

H1b_2 <- res2.H1b$upper.hit.frac*100
H1b_2n <- res2.H1b$lower.hit.frac*100

H1b_3 <- res3.H1b$upper.hit.frac*100
H1b_3n <- res3.H1b$lower.hit.frac*100

H1b_4 <- res4.H1b$upper.hit.frac*100
H1b_4n <- res4.H1b$lower.hit.frac*100

H1b_5 <- res5.H1b$upper.hit.frac*100
H1b_5n <- res5.H1b$lower.hit.frac*100
```

```{r}
H1b_data <- data
H1b_data$Percentage <- c(H1b_1,H1b_2,H1b_3,H1b_4,H1b_5,H1b_1n,H1b_2n,H1b_3n,H1b_4n,H1b_5n)
```

#### Simulation for H1 (Cohen's d=0.8) and BFDA results

```{r}
sim.H1c <- BFDA.sim(expected.ES = 0.8, type="t.paired", n.min=40, n.max=200,  r=sqrt(2)/2, alternative="directional", B=10000, verbose=TRUE, cores=4, stepsize=10, design = "sequential") 

res1.H1c <- BFDA.analyze(sim.H1c, design="sequential", n.max=40, boundary=10)
res2.H1c <- BFDA.analyze(sim.H1c, design="sequential", n.max=80, boundary=10)
res3.H1c <- BFDA.analyze(sim.H1c, design="sequential", n.max=120, boundary=10)
res4.H1c <- BFDA.analyze(sim.H1c, design="sequential", n.max=160, boundary=10)
res5.H1c <- BFDA.analyze(sim.H1c, design="sequential", n.max=200, boundary=10)
```

```{r}
H1c_1<- res1.H1c$upper.hit.frac*100
H1c_1n <- res1.H1c$lower.hit.frac*100

H1c_2 <- res2.H1c$upper.hit.frac*100
H1c_2n <- res2.H1c$lower.hit.frac*100

H1c_3 <- res3.H1c$upper.hit.frac*100
H1c_3n <- res3.H1c$lower.hit.frac*100

H1c_4 <- res4.H1c$upper.hit.frac*100
H1c_4n <- res4.H1c$lower.hit.frac*100

H1c_5 <- res5.H1c$upper.hit.frac*100
H1c_5n <- res5.H1c$lower.hit.frac*100
```

```{r}
H1c_data <- data
H1c_data$Percentage <- c(H1c_1,H1c_2,H1c_3,H1c_4,H1c_5,H1c_1n,H1c_2n,H1c_3n,H1c_4n,H1c_5n)
```

## Simulation parameters for Bayesian correlations:

* n.min = 40 [minimum number of participants]
* n.max = 200 [maximum number of participants]
* expected.ES = 0, 0.1, 0.3, 0.5 [rho]
* Sequential design for linear correlation (directional)
* Uniform prior with parameter a = 1
* boundary = 10 [BF~10~>=10 for H1 and BF~0~>=10, or BF~10~<=1/10, for H0]
* stepsize = 10 [analyses conducted for every 10 participants]
* B = 10000 [number of bootstrap samples]

#### Simulation for H0 (rho=0) and BFDA results

```{r}
cor.H0 <- BFDA.sim(expected.ES = 0, type="correlation", n.min=40, n.max=200,  alpha=1, alternative="directional", B=10000, verbose=TRUE, cores=4, stepsize=10, design = "sequential") 
```

```{r}
cor1.H0 <- BFDA.analyze(cor.H0, design="sequential", n.max=40, boundary=10)
cor2.H0 <- BFDA.analyze(cor.H0, design="sequential", n.max=80, boundary=10)
cor3.H0 <- BFDA.analyze(cor.H0, design="sequential", n.max=120, boundary=10)
cor4.H0 <- BFDA.analyze(cor.H0, design="sequential", n.max=160, boundary=10)
cor5.H0 <- BFDA.analyze(cor.H0, design="sequential", n.max=200, boundary=10)
```

```{r}
corH0_1 <- cor1.H0$upper.hit.frac*100
corH0_1n <- cor1.H0$lower.hit.frac*100

corH0_2 <- cor2.H0$upper.hit.frac*100
corH0_2n <- cor2.H0$lower.hit.frac*100

corH0_3 <- cor3.H0$upper.hit.frac*100
corH0_3n <- cor3.H0$lower.hit.frac*100

corH0_4 <- cor4.H0$upper.hit.frac*100
corH0_4n <- cor4.H0$lower.hit.frac*100

corH0_5 <- cor5.H0$upper.hit.frac*100
corH0_5n <- cor5.H0$lower.hit.frac*100
```

```{r}
corH0_data <- data
corH0_data$Percentage <- c(corH0_1,corH0_2,corH0_3,corH0_4,corH0_5,corH0_1n,corH0_2n,corH0_3n,corH0_4n,corH0_5n)
```

#### Simulation for H1 (rho=0.2) and BFDA results

```{r}
cor.H1a <- BFDA.sim(expected.ES = 0.1, type="correlation", n.min=40, n.max=200,  alpha=1, alternative="directional", B=10000, verbose=TRUE, cores=4, stepsize=10, design = "sequential") 
```

```{r}
cor1.H1a <- BFDA.analyze(cor.H1a, design="sequential", n.max=40, boundary=10)
cor2.H1a <- BFDA.analyze(cor.H1a, design="sequential", n.max=80, boundary=10)
cor3.H1a <- BFDA.analyze(cor.H1a, design="sequential", n.max=120, boundary=10)
cor4.H1a <- BFDA.analyze(cor.H1a, design="sequential", n.max=160, boundary=10)
cor5.H1a <- BFDA.analyze(cor.H1a, design="sequential", n.max=200, boundary=10)
```

```{r}
corH1a_1 <- cor1.H1a$upper.hit.frac*100
corH1a_1n <- cor1.H1a$lower.hit.frac*100

corH1a_2 <- cor2.H1a$upper.hit.frac*100
corH1a_2n <- cor2.H1a$lower.hit.frac*100

corH1a_3 <- cor3.H1a$upper.hit.frac*100
corH1a_3n <- cor3.H1a$lower.hit.frac*100

corH1a_4 <- cor4.H1a$upper.hit.frac*100
corH1a_4n <- cor4.H1a$lower.hit.frac*100

corH1a_5 <- cor5.H1a$upper.hit.frac*100
corH1a_5n <- cor5.H1a$lower.hit.frac*100
```

```{r}
corH1a_data <- data
corH1a_data$Percentage <- c(corH1a_1,corH1a_2,corH1a_3,corH1a_4,corH1a_5,corH1a_1n,corH1a_2n,corH1a_3n,corH1a_4n,corH1a_5n)
```

#### Simulation for H1 (rho=0.5) and BFDA results

```{r}
cor.H1b <- BFDA.sim(expected.ES = 0.3, type="correlation", n.min=40, n.max=200,  alpha=1, alternative="directional", B=10000, verbose=TRUE, cores=4, stepsize=10, design = "sequential") 
```

```{r}
cor1.H1b <- BFDA.analyze(cor.H1b, design="sequential", n.max=40, boundary=10)
cor2.H1b <- BFDA.analyze(cor.H1b, design="sequential", n.max=80, boundary=10)
cor3.H1b <- BFDA.analyze(cor.H1b, design="sequential", n.max=120, boundary=10)
cor4.H1b <- BFDA.analyze(cor.H1b, design="sequential", n.max=160, boundary=10)
cor5.H1b <- BFDA.analyze(cor.H1b, design="sequential", n.max=200, boundary=10)
```

```{r}
corH1b_1 <- cor1.H1b$upper.hit.frac*100
corH1b_1n <- cor1.H1b$lower.hit.frac*100

corH1b_2 <- cor2.H1b$upper.hit.frac*100
corH1b_2n <- cor2.H1b$lower.hit.frac*100

corH1b_3 <- cor3.H1b$upper.hit.frac*100
corH1b_3n <- cor3.H1b$lower.hit.frac*100

corH1b_4 <- cor4.H1b$upper.hit.frac*100
corH1b_4n <- cor4.H1b$lower.hit.frac*100

corH1b_5 <- cor5.H1b$upper.hit.frac*100
corH1b_5n <- cor5.H1b$lower.hit.frac*100
```

```{r}
corH1b_data <- data
corH1b_data$Percentage <- c(corH1b_1,corH1b_2,corH1b_3,corH1b_4,corH1b_5,corH1b_1n,corH1b_2n,corH1b_3n,corH1b_4n,corH1b_5n)
```

#### Simulation for H1 (rho=0.8) and BFDA results

```{r}
cor.H1c <- BFDA.sim(expected.ES = 0.5, type="correlation", n.min=40, n.max=200,  alpha=1, alternative="directional", B=10000, verbose=TRUE, cores=4, stepsize=10, design = "sequential") 
```

```{r}
cor1.H1c <- BFDA.analyze(cor.H1c, design="sequential", n.max=40, boundary=10)
cor2.H1c <- BFDA.analyze(cor.H1c, design="sequential", n.max=80, boundary=10)
cor3.H1c <- BFDA.analyze(cor.H1c, design="sequential", n.max=120, boundary=10)
cor4.H1c <- BFDA.analyze(cor.H1c, design="sequential", n.max=160, boundary=10)
cor5.H1c <- BFDA.analyze(cor.H1c, design="sequential", n.max=200, boundary=10)
```

```{r}
corH1c_1 <- cor1.H1c$upper.hit.frac*100
corH1c_1n <- cor1.H1c$lower.hit.frac*100

corH1c_2 <- cor2.H1c$upper.hit.frac*100
corH1c_2n <- cor2.H1c$lower.hit.frac*100

corH1c_3 <- cor3.H1c$upper.hit.frac*100
corH1c_3n <- cor3.H1c$lower.hit.frac*100

corH1c_4 <- cor4.H1c$upper.hit.frac*100
corH1c_4n <- cor4.H1c$lower.hit.frac*100

corH1c_5 <- cor5.H1c$upper.hit.frac*100
corH1c_5n <- cor5.H1c$lower.hit.frac*100
```

```{r}
corH1c_data <- data
corH1c_data$Percentage <- c(corH1c_1,corH1c_2,corH1c_3,corH1c_4,corH1c_5,corH1c_1n,corH1c_2n,corH1c_3n,corH1c_4n,corH1c_5n)
```

##### Plots used in Stage 1 RR manuscript [manually edited further for A/B panel format]

```{r}
#Combine all data together and add a column for effect sizes
all_data <-rbind(H0_data,H1a_data,H1b_data,H1c_data)
all_data$Effect <- c(rep("0",times=10), rep("0.2",times=10), rep("0.5",times=10), rep("0.8",times=10))

write.csv(all_data, "BFDA_results_ttest.csv")
```

```{r}
multi_plot <- ggplot(data=all_data, aes(y=Percentage, x=Sample_size, shape=Boundary, fill=Boundary)) + xlim(40,200) + ylim(0,100) + geom_line(size=0.6, color="#737373") + geom_point(size=1.8, color="#737373") + theme_gray(base_size=16, base_family = 'Palatino') + scale_x_continuous('\nSample size', breaks=c(40,80,120,160,200), minor_breaks = NULL)+ scale_y_continuous("Studies terminating at a boundary (%)\n",limits = c(0,100))+ theme(plot.title = element_text(hjust = 0.5, size=16, face="bold")) + facet_wrap(~Effect, nrow=1, shrink=FALSE, labeller = label_bquote("Cohen's"~italic(.("d")["z"])~"="~.(Effect))) + theme(legend.position = "top", legend.title = element_blank(), legend.key = element_rect(size = 6), legend.key.size = unit(2, 'lines')) +  scale_shape_manual(name="Boundary",labels=c("H0", "H1"),values = c(21, 23)) + scale_fill_manual(name="Boundary",labels=c("H0", "H1"),values=c("#F67861","#96317F")) 

multi_plot 

ggsave("BFDA_plot_A.png", dpi = 600, height = 5, width = 8)
```

```{r}
cor_data <-rbind(corH0_data,corH1a_data,corH1b_data,corH1c_data)
cor_data$Effect <- c(rep("0",times=10), rep("0.1",times=10), rep("0.3",times=10), rep("0.5",times=10))

write.csv(cor_data, "BFDA_results_correlation.csv")
```

```{r}
multi_cor_plot <- ggplot(data=cor_data, aes(y=Percentage, x=Sample_size, shape=Boundary,fill=Boundary)) + xlim(40,200) + ylim(0,100) + geom_line(size=0.6, color="#737373") + geom_point(size=1.8, color="#737373") + theme_gray(base_size=16, base_family = 'Palatino') + scale_x_continuous('\nSample size', breaks=c(40,80,120,160,200), minor_breaks = NULL)+ scale_y_continuous("Studies terminating at a boundary (%)\n",limits = c(0,100))+ theme(plot.title = element_text(hjust = 0.5, size=16, face="bold")) + scale_color_manual(values=c("#F67861","#96317F"), breaks=c("H1","H0"), guide_legend(title="")) + theme(legend.position = "top", legend.title=element_blank(), legend.key = element_rect(size = 6), legend.key.size = unit(2, 'lines')) + facet_wrap(~Effect, nrow=1, ncol=4, shrink=FALSE, labeller = label_bquote("Correlation"~rho~"="~.(Effect)))+  scale_shape_manual(name="Boundary",labels=c("H0", "H1"),values = c(21, 23)) + scale_fill_manual(name="Boundary",labels=c("H0", "H1"),values=c("#F67861","#96317F")) 

multi_cor_plot 

ggsave("BFDA_plot_B.png", dpi = 600, height = 5, width = 8)
```




